\begin{lem} \label{lem:local_wrt_directed_complexes}
    Let \( C \) be a stricter \( n \)\nbd category and \( P \) be a \( n \)\nbd regular directed complex.
    Then \( C \) is local with respect to the canonical strict functor 
    \begin{equation*}
        s_P \colon \colim_{x \in P} \molecin{\imel{P}{x}} \to \molecin{P}.
    \end{equation*}
\end{lem}
\begin{proof}
    Consider a strict functor \( \F \colon \colim_{x \in P} \molecin{\imel{P}{x}} \to C \), and for \( x \in P \), denote by \( \F_x \) the restriction of \( \F \) along \( \molecin{\imel{P}{X}} \to \colim_{x \in P} \molecin{\imel{P}{x}} \).
    We define a strict functor \( \G \colon \molecin{P} \to C \) such that \( \G \after s_P = \F \).
    Let \( u \colon U \to P \) be a morphism with \( U \) an atom.
    Then \( u = \mapel{x} \) for some \( x \in P \), hence we must necessarily let \( \G(u) \eqdef \F_x(\idd{}) \).
    Since \( \atomin{P} \) is a basis for \( \molecin{P} \), this assignment uniquely determine \( \G \).
    We need to show that this indeed makes \( \G \) a strict functor.
    Let \( w \colon W \to P \) be a pasting diagram.
    We show that \( \G(w) \) does is independent on the decomposition of \( w \) into pasting of cells. 
    We proceed by induction on submolecules, the base case being evident.
    Inductively, suppose that \( \G(w') \) is well defined for all proper subdiagrams \( w' \) of \( w \), and consider a proper decomposition \( w = w_1 \cp{k} w_2 \).
    Then we have a strict functor \( (\G_1, \G_2) \colon \molecin{W_1} \cup \molecin{W_2} \to C \), where \( \G_i \) is the restriction of \( \G \) along \( \molecin{w_i} \), which is well defined by inductive hypothesis. 
    Since \( C \) is stricter, \( (\G_1, \G_2) \) extends to a strict functor \( \G' \colon \molecin{W} \to C \) with the property that \( \G'(u) = \G(u) \) for all \( u \in \atomin{P} \).
    This proved that \( \G \) is well defined, and concludes the proof. 
\end{proof}


\begin{prop} \label{prop:density_of_pasting_diagram}
    Let \( C \) be a stricter \( \omega \)\nbd category.
    Then the canonical strict functor
    \begin{equation*}
        \phi \colon \colim_{u \in \Dgm(C)} \molecin{U} \to C,
    \end{equation*}
    is an isomorphism.
\end{prop}
\begin{proof}
    We show that \( C \) has the universal property of the colimit. 
    Consider a cone \( \set{\F_u \colon \molecin{U} \to D}_{u \in \Dgm(C)} \) for some stricter \( \omega \)\nbd category \( D \).
    We define a strict functor \( \F \colon C \to D \).
    Each globular cell \( c \) of \( C \) is classifies by a pasting diagram \( u \colon O^n \to C \), and therefore we must let \( \F(c) \eqdef \pcell{\F_u} \).
    This shows the uniqueness of the universal property.
    Let \( U \) be a molecule. 
    We must show that the diagram
    \begin{center}
        \begin{tikzcd}
            {\molecin{U}} \\
            C & D
            \arrow["u"', from=1-1, to=2-1]
            \arrow["{\F_u}", from=1-1, to=2-2]
            \arrow["\F"', from=2-1, to=2-2]
        \end{tikzcd}
    \end{center}
    commute.
    Let \( w \colon W \to U \) be a morphism with \( \dim w = n \).
    Then \( w \) is classified by a pasting diagram \( w' \colon \globe{n} \to \molecin{U} \), and by definition, \( \F \after u \after w' = \F_u \after w' \).
    Passing to the principal cells, we get that \( (\F \after u)(w) = \F_u(w) \).
    This shows that the diagram commutes.
    Now we need to proves that \( \F \) is indeed a strict functor, which is done by using the fact that \( C \) is stricter, the commutation of the previous diagram for all molecules \( U \), together with the strict functors
    \begin{equation*}
        \molecin{(\bd{k}{\a} \dglobe{n})} \to \molecin{\dglobe{n}}
    \end{equation*}
    classifying the morphism \( \bd{k}{\a} \dglobe{n} \to \dglobe{n} \), and  
    \begin{equation*}
        \molecin{\dglobe{n}} \to \molecin{(\dglobe{n} \cp{k} \dglobe{n})},
    \end{equation*}
    classifying the principal cell of \( \molecin{(\dglobe{n} \cp{k} \dglobe{n})} \).
    This concludes the proof.
\end{proof}

\begin{rmk} \label{rmk:thetas_are_dense}
    As it is the case for strict \( \omega \)\nbd categories, the previous result is still valid if one let the colimit run over pasting diagrams \( u \colon \molecin{U} \to C \), where \( U \) is a ``theta'', that is, a pasting of directed globes.
\end{rmk}


%% old folk model structure



% \begin{lem} \label{lem:j_n_weak_equivalence_cofibration}
%     Let \( n \geq 0 \).
%     Then \( j_n \) is both a stricter cofibration and an \( \omega \)\nbd equivalence.
% \end{lem}
% \begin{proof}
%     The strict functor \( j_n \) is a stricter cofibration as composite of two stricter cofibrations.
%     Furthermore, \( p \after j_n = \idd{\globe{n}} \).
%     By \cite[Proposition 20.1.17 and 20.1.13 ]{ara2025polygraphs} (which hold more generally for strict functors of composition structures), \( j_n \) is an \( \omega \)\nbd equivalence.
% \end{proof}

    % A globular \( n \)\nbd cell \( u \) in \( \Gamma(C) \) is therefore a strict functor \( u \colon \molec{(\arr \gray \dglobe{n})} \to C \), and we say that \( u \) is a \emph{reversible cylinder} if \( \pcell{u} \), as well as the principal cells of 
    % \begin{equation*}
    %    u \after \molecin{(\arr \gray \iota^\a_k)} \colon \molecin{(\arr \gray \dglobe{k})} \to C
    % \end{equation*}
    % are reversible, for each \( k \geq 0 \) and \( \a \in \set{-, +} \), where \( \iota^\a_k \) is the strict functor
    % \begin{equation*}
    %     \iota^\a_k \colon \molecin{(\bd{k}{\a} \dglobe{n})} \to \molecin{\dglobe{n}}.
    % \end{equation*} 
    % We then define the \emph{stricter \( \omega \)\nbd category of reversible cylinder} \( \rGamma(C) \) to be the stricter \( \omega \)\nbd category \( \rGamma(C) \subseteq \Gamma(C) \) on globular cells classifying reversible cylinders.

    % \begin{prop} \label{lem:stricter_cof_and_weak_stable_under_pushout}
%     The class of strict functors between stricter \( \omega \)\nbd categories that are both \( \omega \)\nbd equivalences and stricter cofibrations is closed under pushouts (in \( \somegaCat \)).
% \end{prop}
% \begin{proof}
%     Similar to the proof of \cite[Theorem 20.5.6]{ara2025polygraphs}, replacing ``cofibration'' with ``stricter cofibrations''.
% \end{proof}

\begin{dfn} [Relative stricter polygraph and stricter cofibration]
    Let \( f \colon C \to D \) be a strict functor of stricter \( \omega \)\nbd categories.
    We say that \( f \) is a \emph{relative stricter polygraph} if \( f \) can be written as a transfinite composition of pushouts (in \( \somegaCat \)) of elements of \( \Icof \).
    A retract of a relative stricter polygraph is called a \emph{stricter cofibration}.
\end{dfn}