\section{Stricter \texorpdfstring{$\omega$}{ω}-categories} \label{sec:stricter}

\subsection{Definitions and properties}

\begin{dfn} [Reflexive \( \omega \)\nbd graph]
    A \emph{reflexive \( \omega \)\nbd graph} is a set \( C \), whose element are called the \emph{globular cells}, together with, for each \( k \in \mathbb{N} \), operators
    \begin{equation*}
        \bd{k}{-}, \bd{k}{+} \colon C \to C,
    \end{equation*}
    called the \emph{input and output \( k \)\nbd boundary operators}, respectively, satisfying the following axioms:
    \begin{enumerate}
        \item for all \( c \in C \), there exists \( k \in \mathbb{N} \) such that \( \bd{k}{-} c = c = \bd{k}{+} c \); the \emph{dimension of \( c \)}, written \( \dim c \), is the minimum of all such values of \( k \);
        \item for all \( c \in C \), all \( k, n \geq 0 \) and all \( \a, \beta \in \set{-, +} \),
        \begin{equation*}
            \bd{k}{\a}(\bd{n}{\beta} c) = 
            \begin{cases}
                \bd{k}{\a} c & \text{if }k < n, \\
                \bd{n}{\beta} c& \text{else.}
            \end{cases}
        \end{equation*}
    \end{enumerate}
    A \emph{morphism of reflexive \( \omega \)\nbd graphs} is a function of the underlying set commuting with the boundary operators.

    If \( C \) is a reflexive \( \omega \)\nbd graph, the set of \emph{\( k \)\nbd composable pairs of globular cells} is the set 
    \begin{equation*}
        C \times_k C \eqdef \set{(c, d) \in C \times C \mid \bd{k}{+} c = \bd{k}{-} d}.
    \end{equation*}
    Given a globular cell \( c \) and \( \a \in \set{-, +} \), we write \( \bd{}{\a} c \) in place of \( \bd{\dim c - 1}{\a} c \).
    We say that a globular cell \( c \) is an \emph{object} if \( \dim c = 0 \). 
\end{dfn}

\begin{dfn} [Composition structure]
    A composition structure is a reflexive \( \omega \)\nbd graph \( C \) together with, for all \( k \in \mathbb{N} \), an operation
    \begin{equation*}
        - \comp{k} - \colon C \times_k C \to C,
    \end{equation*}
    call the \emph{\( k \)\nbd composition operation}.
    If \( C, D \) are composition structures, a \emph{strict functor} \( \F \colon C \to D \) is a morphism of the underlying reflexive  \( \omega \)\nbd graphs respecting the \( k \)\nbd composition operations, for all \( k \in \mathbb{N} \).
    We denote \( \Comp \) the category of composition structures and strict functors.
\end{dfn}

\begin{rmk}
    The category \( \Comp \) is equivalent to a category of models of a limit sketch; using for instance a simpler version of \cite[Proposition 14.2.4]{ara2025polygraphs}.
    In particular, it is locally presentable, complete, and cocomplete \cite{adamek1994locally}.
\end{rmk}

\begin{dfn} [Basis for composition structure]
    Let \( C \) be a composition structure, and \( \cls{S} \) be a subset of the globular cells of \( C \).
    We say that \( \cls{S} \) is a \emph{generating set for \( C \)} if the closure of \( \cls{S} \) under the operations \( \set{- \comp{k} -}_{k \in \mathbb{N}} \) is equal to \( C \).
    We say that a generating set is a \emph{basis for \( C \)} if for any other generating set \( \cls{T} \) such that \( \cls{T} \subseteq \cls{S} \), then \( \cls{T} = \cls{S} \).
\end{dfn}

\begin{lem}\label{lem:strict_functor_determined_by_basis}
    Let \( f, g \colon C \to D \) be strict functors of composition structures and let \( \cls{S} \) be a generating set for \( C \) such that for all \( c \in \cls{S} \), \( f(c) = g(c) \).
    Then \( f = g \).
\end{lem}
\begin{proof}
    See \cite[Lemma 5.1.23]{hadzihasanovic2024combinatorics}.
\end{proof}

\begin{dfn} [Molecules in a regular directed complexes]
    Let \( P \) be a regular directed complex.
    We let \( \molecin{P} \) to be the composition structure whose
    \begin{itemize}
        \item globular cells are the local embedding \( u \colon U \to P \) with \( U \) a molecule;
        \item boundary operators are defined by \( u \mapsto \bd{k}{ \a} u \), for all \( k \in \mathbb{N} \) and \( \a \in \set{-, +} \);
        \item the \( k \)\nbd composition operation is given by the pasting \( (u, v) \mapsto u \cp{k} v \), for all \( k \in \mathbb{N} \). 
    \end{itemize}    
\end{dfn}

\begin{rmk}
    Since isomorphisms of molecules are unique when they exist, we always identify two isomorphic objects \( u \colon U \to P \) and \( u' \colon U' \to P \) in \( \molecin{P} \).
\end{rmk}

\noindent Recall from \cite[Proposition 5.2.7, Theorem 6.2.35, Theorem 6.3.17]{hadzihasanovic2024combinatorics} that the subset \( \atomin{P} \) of \( \molecin{P} \) on local embeddings \( u \colon U \to P \) whose domain is an atom, is a basis for \( \molecin{P} \), and the assignment \( P \mapsto \molecin{P} \) extends to functors
\begin{align*}
    \molecin{-} &\colon \rdcpxmap \to \Comp \\
    \molecin{-} &\colon \opp{\rdcpxcomap} \to \Comp.   
\end{align*} 

\begin{dfn} [Globe]
    Let \( n \geq 0 \).
    The \emph{\( n \)\nbd globe} is the composition structure defined by \( \globe{n} \eqdef \molecin{\dglobe{n}} \), and its \emph{boundary} is the composition structure given by \( \bd{}{}\globe{n} \eqdef \molecin{(\bd{}{}\dglobe{n})} \).
\end{dfn}

\begin{dfn} [Pasting diagram in a composition structure]
    Let \( C \) be a composition structure and \( U \) be a molecule.
    A \emph{pasting diagram of shape \( U \) in \( C \)} is a strict functor \( u \colon \molecin{U} \to C \).
    If \( U \) is an atom, we say that \( u \) is a \emph{cell}.
    We let \( \dim u \eqdef \dim U \), and for \( k \geq 0 \) and \( \a \in \set{-, +} \), we write \( \bd{k}{\a} u \) for the restriction of \( u \) along the strict functor \( \molecin{\bd{k}{\a} U} \to \molecin{U} \), and may omit \( k \) when it is equal to \( \dim u - 1 \).
    Finally, we write \( u \colon u^- \celto u^+ \) to mean that \( \bd{}{\a} u = u^\a \), for all \( \a \in \set{-, +} \), and call \( u^- \celto u^+ \) the \emph{type} of \( u \).
    Two pasting diagrams are \emph{parallel} if they have the same type.
    A \emph{subdiagram of a pasting diagram \( u \colon \molecin{U} \to C \)} is the data of a pasting diagram \( v \colon \molecin{V} \to C \) together with a submolecule inclusion \( \iota \colon V \submol U \) such that \( u \after \molecin{\iota} = v \).
    We write \( \iota \colon v \submol u \) for the data of a subdiagram.
\end{dfn}

\begin{dfn} [Principal cell]
    Let \( \F \colon \molecin{U} \to C \) be a pasting diagram, and \( c \) be a globular cell of \( C \).
    We say that \emph{\( \F \) classifies \( c \)} if \( \F(\idd{U}) = c \).
    In that case, \( c \) is called the \emph{principal cell of \( \F \)} and is written \( \pcell{\F} \).
\end{dfn}

\begin{comm}
    We warn the reader on the difference between cells and globular cells. 
    A globular cell \( c \in C \) of dimension \( n \geq 0 \) is classified uniquely by the cell \( u \colon \globe{n} \to C \) such that \( \pcell{u} = c \).
    Conversely, a cell \( u \colon \globe{n} \to C \) factors uniquely as \( v \after \molecin{\tau} \), where \( \tau \colon \dglobe{n} \surj \dglobe{\dim \pcell{u}} \) is the unique surjection of atoms, and \( v \colon \globe{\dim \pcell{u}} \to C \) classifies \( \pcell{u} \).
\end{comm}

\begin{dfn}
    For each regular directed complex \( P \), there is a canonical strict functor
    \begin{equation*}
        s_P \colon \colim_{x \in P} \molecin{\imel{P}{x}} \to \molecin{P},
    \end{equation*}
    where the colimit is computed in \( \Comp \).
    We let \( S \) be the set
    \begin{equation*}
        S \eqdef \set{s_P \colon \colim_{x \in P} \molecin{\imel{P}{x}} \to \molecin{P} \mid P \text{ finite regular directed complex}}.
    \end{equation*}
\end{dfn}

\begin{dfn}[Stricter \( \omega \)\nbd category] \label{dfn:stricter_omega_cat}
    A \emph{stricter \( \omega \)\nbd category} is a composition structure which is local with respect to \( S \).
    We let \( \somegaCat \) be the full subcategory of \( \Comp \) on stricter \( \omega \)\nbd categories.
\end{dfn}

\noindent Since \( \Comp \) is locally presentable and \( S \) is a small set, the full subcategory inclusion \( \iota \colon \somegaCat \incl \Comp \) is reflective \cite{freyd1972continuous}, and we denote by 
\begin{equation*}
    \rc \colon \Comp \to \somegaCat
\end{equation*}
the left adjoint of \( \iota \).

\begin{dfn} [Matching family and amalgamation]
    Let \( P \) be a regular directed complex and \( C \) be a composition structure.
    A \emph{\( P \)\nbd matching family in \( C \)} is a cone 
    \begin{equation*}
        \set{\F_x \colon \molecin{\imel{P}{x}} \to C}_{x \in P}
    \end{equation*}
    under the \( P \)\nbd shaped diagram \( x \mapsto \molecin{\imel{P}{x}} \).    
    An \emph{amalgamation} of this matching family is a strict functor 
    \begin{equation*}
        \amalg_{x\in P} \F_x \colon \molecin{P} \to C
    \end{equation*}
    such that, for all \( y \in P \), \( (\amalg_x \F_x) \after \molecin{\mapel{y}} = \F_y \).
\end{dfn}

\begin{rmk}
    Thus, a composition structure \( C \) is a stricter \( \omega \)\nbd category if for all finite regular directed complex \( P \), all \( P \)\nbd matching families in \( C \) have a unique amalgamation.
\end{rmk}

\begin{rmk}\label{rmk:data_matching family}
    The data of a \( P \)\nbd matching family 
    \begin{equation*}
        \set{\F_x \colon \molecin{\imel{P}{x}} \to C}_{x \in P}
    \end{equation*}
    in \( C \) is given by a family of globular cells \( \set{c_x \in C}_{x \in P} \).
    Indeed, given a matching family \( \set{\F_x}_{x \in P} \), define \( c_x \eqdef \pcell{\F_x} \).
    By functoriality, if \( x \le y \), then \( c_x = \F_y(\imel{P}{x} \incl \imel{P}{y}) \).
    Since \( \atomin{\imel{P}{y}} \) is a basis for \( \molecin{\imel{P}{y}} \), Lemma \ref{lem:strict_functor_determined_by_basis} implies that the data of \( \set{c_x}_{x \in \imel{P}{y}} \) entirely determines \( \F_y \colon \molecin{\imel{P}{y}} \to C \).
    Of course, not all data of this type give rise to a matching family. 
\end{rmk}

\begin{lem}\label{lem:at_most_one_lift}
    Let \( C \) be a composition structure, \( P \) be a regular directed complex, and \( \set{\F_x}_{x \in P} \) be a matching family. 
    Then \( \set{\F_x}_{x \in P} \) has at most one amalgamation.
\end{lem}
\begin{proof}
    Immediate by Lemma \ref{lem:strict_functor_determined_by_basis}.
\end{proof}

\begin{lem} \label{lem:well_define_from_regular_iff_well_defined_from_molecules}
    Let \( C \) be a composition structure, \( P \) be a regular directed complex, \( \set{\F_x \colon \molecin{\imel{P}{x}} \to C}_{x \in P} \) be a \( P \)\nbd matching family in \( C \). 
    Suppose that for all \( w \colon W \to P \) in \( \molecin{P} \), the \( W \)\nbd matching family \( \set{\F_{w(y)} \colon \imel{P}{w(y)} \to X}_{y \in W} \) in \( C \) has a well-defined amalgamation.
    Then \( \set{\F_x}_{x \in P} \) has a well-defined amalgamation.
\end{lem}
\begin{proof}
    For \( w \colon W \to P \) in \( \molecin{P} \), we let \( \F_w \) be the strict functor 
    \begin{equation*}
        \amalg_{y \in W} \F_{w(y)} \colon \molecin{W} \to C
    \end{equation*}
    We claim that \( \F \colon \molecin{P} \to C \) defined by \( w \mapsto \pcell{\F_w} \) is a strict functor.
    By construction, \( \F \) is a morphism of the underlying reflexive \( \omega \)\nbd graphs.
    Let \( w \colon W \to P \) in \( \molecin{P} \), and suppose that \( w = w^- \cp{k} w^+ \) for some \( k \geq 0 \) and \( w^\a \colon W^\a \to P \) in \( \molecin{P} \), for all \( \a \in \set{-, +} \).
    Then
    \begin{equation*}
        \pcell{\F_w} = \F_w(W^- \incl W) \comp{k} \F_w(W^+ \incl W) = \pcell{\F_{w^-}} \comp{k} \pcell{\F_{w^+}}.
    \end{equation*}
    Thus \( \F(w) = \F(w^-) \comp{k} \F(w^+) \).
    This concludes the proof.
\end{proof}

\begin{comm} \label{comm:well_defined_amalgamation}
    Given a \( P \)\nbd matching family \( \set{\F_x} \) in \( C \), we thus have a \emph{candidate amalgamation} \( \F \colon \molecin{P} \to C \) defined on the basis \( \atomin{P} \) by \( \mapel{x} \mapsto \pcell{\F_x} \).
    Then, \( \F \) is a well-defined strict functor if for all local embeddings \( u \colon U \to P \) with \( U \) a molecule, if \( u = u_1 \cp{k} u_2 \), then \( \F(u) = \F(u_1) \comp{k} \F(u_2) \).
    To show this, we may use \emph{induction on submolecules} (see \cite[Comment 4.1.7]{hadzihasanovic2024combinatorics}) as follows.
    Take an arbitrary element \( w \colon W \to P \) in \( \molecin{P} \), and prove that \( \F \after \molecin{w} \) is a well-defined strict functor under the hypothesis that for all proper subdiagrams \( \iota \colon W' \submol W \) of \( W \), \( \F \after \molecin{w \after \iota} \) is a well-defined strict functor.
    The base case on submolecules \( W' \) of \( W \) of dimension \( 0 \) is always true in that case. 
\end{comm}

\begin{lem} \label{lem:stricter_iff_local_wrt_pasting}
    Let \( C \) be composition structure.
    The following are equivalent.
    \begin{enumerate}
        \item \( C \) is a stricter \( \omega \)\nbd category;
        \item for all molecules \( U \), \( C \) is local with respect to \( s_U \);
        \item for all regular directed complexes \( P \), \( C \) is local with respect to \( s_P \);
        \item for all pairs of molecules \( U, V \), and \( k \in \mathbb{N} \) such that \( U \cp{k} V \) is defined, each lifting problem
        \begin{center}
            \begin{tikzcd}
                {\molecin{U} \cup \molecin{V}} & C \\
                {\molecin{(U \cp{k} V)}}
                \arrow[from=1-1, to=1-2]
                \arrow[from=1-1, to=2-1]
            \end{tikzcd}
        \end{center}
        has a (necessarily unique) solution.
    \end{enumerate}
\end{lem}
\begin{proof}
    The equivalences between the first three points directly follows from Lemma \ref{lem:at_most_one_lift} and Lemma \ref{lem:well_define_from_regular_iff_well_defined_from_molecules}.
    Next, the last condition is clearly necessary, since any functor \( \molecin{U} \cup \molecin{V} \to C \) defines in particular a \( (U \cp{k} V) \)\nbd matching family in \( C \).
    Conversely, we show it is sufficient.
    Let \( P \) be a regular directed complex.
    We show that \( C \) is local with respect to \( s_P \).
    Let \( \set{\F_x}_{x \in P} \) be a \( P \)\nbd matching family in \( C \).
    We show that the candidate amalgamation \( \F \colon \molecin{P} \to C \) is a strict functor as per Comment \ref{comm:well_defined_amalgamation}.
    Let \( w \colon W \to P \) in \( \molecin{P} \), and suppose that \( \F \after \molecin{w \after \iota} \) is well-defined for all proper submolecules \( \iota \colon W' \submol W \) of \( W \).
    Then either \( w \) is in \( \atomin{P} \), in which cases we are done since \( \F \after \molecin{w} = \F_x \) for the unique \( x \in P \) such that \( w = \mapel{x} \), or \( w = w_1 \cp{k} w_2 \) for some local embeddings \( w_1 \colon W_1 \to P \) and \( w_2 \colon W_2 \to P \).
    Then, by inductive hypothesis, we have a strict functor \( (\F \after \molecin{w_1}, \F \after \molecin{w_2}) \colon \molecin{W_1} \cup \molecin{W_2} \to C \).
    By hypothesis, this extends to a strict functor \( \F' \colon \molecin{(W_1 \cp{k} W_2)} \to C \), which is equal to \( \F \after \molecin{w} \) by Lemma \ref{lem:strict_functor_determined_by_basis}.
    This shows that \( \F \after \molecin{w} \) is well-defined and concludes the proof.
\end{proof}

\begin{prop} \label{prop:regular_directed_complex_stricter}
    Let \( P \) be a regular directed complex.
    Then \( \molecin{P} \) is a stricter \( \omega \)\nbd category.
\end{prop}
\begin{proof}
    Let \( Q \) be a regular directed complex, and consider a \( Q \)\nbd matching family \( \set{\F_x \colon \molecin{\imel{Q}{x}} \to \molecin{P}}_{x \in Q} \) in \( \molecin{P} \).
    We want to show that the candidate amalgamation \( \F \colon \molecin{Q} \to \molecin{P} \) is well-defined. 
    For each \( w \colon W \to Q \) in  \( \molecin{Q} \), \( \F(w) \) is given by the canonical local embedding \( \colim_{y \in W} \pcell{\F_{w(y)}} \to P \), which is independent of the chosen decomposition of \( w \).
    This concludes the proof.
\end{proof}

\noindent Therefore, the functor \( \molecin{-} \colon \rdcpxmap \to \Comp \) factors through the subcategory \( \somegaCat \).

\begin{cor} \label{cor:regular_directed_complex_colimit_of_itself}
    Let \( P \) be a regular directed complex.
    Then in \( \somegaCat \),
    \begin{equation*}
        s_P \colon \colim_{x \in P} \molecin{\imel{P}{x}} \cong \molecin{P}.
    \end{equation*}
\end{cor}
\begin{proof}
    By Lemma \ref{lem:stricter_iff_local_wrt_pasting}, \( \rc(s_P) \) is an isomorphism in \( \somegaCat \).
    Since \( \rc \) is left adjoint, we conclude by Proposition \ref{prop:regular_directed_complex_stricter}.
\end{proof}

\begin{cor} \label{cor:molecin_preserves_pushout_inclusions}
    The functor \( \molecin{-} \colon \rdcpxmap \to \somegaCat \) preserves all pushouts of inclusions. 
\end{cor}

\begin{dfn} [Stricter \( n \)\nbd category]
    Let \( n \in \mathbb{N} \).
    An \emph{\( n \)\nbd composition structure} is a composition structure \( C \) such that for all globular cells \( c \in C \), we have \( \dim c \le n \).
    If \( C \) was a stricter \( \omega \)\nbd category, we speak of \emph{stricter \( n \)\nbd category}.
    We denote by \( \nComp{n} \) and \( \snCat{n} \) the full subcategories of \( \Comp \) and \( \somegaCat \) on \( n \)\nbd composition structures and stricter \( n \)\nbd categories, respectively. 
\end{dfn}

\begin{dfn} 
    Let \( n \in \mathbb{N} \).
    The inclusion \( \iota_n \colon \nComp{n} \incl \Comp \) has a right adjoint \( \skel{n} \) defined by
    \begin{equation*}
        \skel{n}(C) \eqdef \set{c \in C \mid \dim c \le n},
    \end{equation*}
    and a left adjoint \( \trunc{n} \) defined by
    \begin{equation*}
        \trunc{n}(C) \eqdef \skel{n - 1}(C) \cup \set{[c] \mid c \in C, \dim c = n},
    \end{equation*}
    where \( [-] \) denotes the equivalence class on the globular cells of \( C \) of dimension \( n \) generated by \( \bd{}{-} d \sim \bd{}{+} d \), for all globular cells \( d \) of dimension \( n + 1 \). 
    By convention, \( \skel{-1}(C) = \varnothing \).
    It is also convenient to let \( \trunc{\omega} \) be the identity.
\end{dfn}

\begin{rmk}
    By \cite[Proposition 5.2.14]{hadzihasanovic2024combinatorics}, if \( P \) is a regular directed complex, \( \skel{n} \molecin{P} \) is naturally isomorphic to \( \molecin{(\gr{\le n}P)} \).
\end{rmk}

\begin{lem} \label{lem:stricter_n_iff_local_with_dim_le_n}
    Let \( C \) be an \( n \)\nbd composition structure.
    The following are equivalent.
    \begin{enumerate}
        \item \( C \) is a stricter \( n \)\nbd category;
        \item for all molecules \( U \) with \( \dim U \le n \), \( C \) is local with respect to \( s_U \);
        \item for all regular directed complexes with \( \dim P \le n \), \( C \) is local with respect to \( s_P \);
        \item for all pairs of molecules \( U, V \) with \( \dim U, \dim V \le n \) and \( k \in \mathbb{N} \) such that \( U \cp{k} V \) is defined, each lifting problem
            \begin{center}
                \begin{tikzcd}
                    {\molecin{U} \cup \molecin{V}} & C \\
                    {\molecin{(U \cp{k} V)}}
                    \arrow[from=1-1, to=1-2]
                    \arrow[from=1-1, to=2-1]
                \end{tikzcd}
            \end{center}
            has a (necessarily unique) solution.
    \end{enumerate}
\end{lem}
\begin{proof}
    The second and third condition are equivalent by Lemma \ref{lem:well_define_from_regular_iff_well_defined_from_molecules}.
    Suppose \( C \) is a stricter \( n \)\nbd category.
    In particular, \( C \) is a stricter \( \omega \)\nbd category, so by Lemma \ref{lem:stricter_iff_local_wrt_pasting}, the second and third conditions hold.
    Now suppose the third condition holds, consider a regular directed complex \( P \) and a \( P \)\nbd matching family \( \set{\F_x \colon \molecin{\imel{P}{x}} \to C} \) with candidate amalgamation \( \F \).
    Restricting this matching family to \( \set{\F_x}_{x \in \gr{\le n}{P}} \), and using the assumption, we have an amalgamation 
    \begin{equation*}
        \gr{\le n}{\F} \eqdef \amalg_{x \in \gr{\le n}{P}} \F_x \colon \gr{\le n}{P} \to C.
    \end{equation*}
    Let \( x \in P \) with \( \dim x > n \).
    Then \( \dim \pcell{\F_x} \le n \), hence for any \( \a \in \set{-, +} \), \( \pcell{\bd{n}{\a} \F_x} = \pcell{\F(\bd{n}{\a} x \to P)} \).
    Using this fact, an induction on the submolecules of any \( w \colon W \to P \) shows that \( \F(w) = \gr{\le n}{\F}(\bd{n}{\a} w) \), proving that \( \F \) is well-defined.
    This shows that \( C \) is stricter.
    The last condition is shown equivalent to the third one using a similar argument as in the proof of Lemma \ref{lem:stricter_iff_local_wrt_pasting}.
    This concludes the proof.
\end{proof}

\begin{lem} \label{lem:truncation_stricter_are_stricter}
    Let \( n \geq 0 \), and \( C \) be a stricter \( \omega \)\nbd category.
    Then \( \skel{n}(C) \) and \( \trunc{n}(C) \) are stricter \( n \)\nbd categories.
\end{lem}
\begin{proof}
    We use the third point of Lemma \ref{lem:stricter_n_iff_local_with_dim_le_n}.
    Let \( P \) be a regular directed complex with \( \dim P \le n \), and \( \set{\F_x \colon \molecin{\imel{P}{x}} \to \skel{n}(C)}_{x \in P} \) be a \( P \)\nbd matching family in \( \skel{n}(C) \).
    Then post-composing each \( \F_x \) by the counit \( \counit_C \colon \skel{n}(C) \to C \) defines a \( P \)\nbd matching family \( \set{\counit \after \F_x}_{x \in P} \) in \( C \).
    Since \( C \) is stricter, it has an amalgamation \( \F' \colon \molecin{P} \to C \).
    Then, since \( \skel{n}(P) = P \), \( \skel{n}(\F') \) is the desired amalgamation of the matching family \( \set{\F_x}_x \).

    Now consider a \( P \)\nbd matching family \( \set{\G_x \colon \molecin{\imel{P}{x}} \to \trunc{n}(C)}_{x \in P} \) in \( \trunc{n}C \).
    By definition of \( \trunc{n}(C) \), and since \( \skel{n - 1}(C) \subseteq \trunc{n}(C) \) is stricter, we have by the first part of the proof the amalgamation
    \begin{equation*}
        \gr{< n }{\G} \eqdef \amalg_{x \in \gr{< n}{P}} \G_x \colon \molecin{\gr{< n}{P}} \to \trunc{n}(C).
    \end{equation*}
    For each \( x \in P \), choose a representative \( c_x \in C \) of the cell \( \pcell{\G_x} \) in \( \trunc{n}(C) \) (if \( \dim \pcell{\G_x} \le n \), then we mean that we let \( c_x \eqdef \pcell{\G_x} \)).
    We claim that \( \set{c_x}_{x \in P} \) give rise to a matching family \( \set{\G'_x \colon \molecin{\imel{P}{x}} \to C}_{x \in P} \), as per Remark \ref{rmk:data_matching family}.
    This is clear for all \( x \in \gr{< n}{P} \), since this is the data associated to the matching family \( \set{\G_x}_{x \in \gr{< n}{P}} \). 
    If \( \dim x = n \), then we claim that \( \bd{}{}\G'_x \colon \molecin{\bd{}{}\imel{P}{x}} \to C \) extends to a strict functor \( \G'_x \colon \molecin{\imel{P}{x}} \to C \) by letting \( \idd{x} \mapsto c_x \).
    Indeed, for all \( k < n \) and \( \a \in \set{-, +} \), we have \( \bd{k}{\a} c_x = \gr{< n}{G}(\bd{k}{\a} \mapel{x} ) \), since the former is independent of the chosen representative \( c_x \) of \( \pcell{\G_x} \).
    Thus \( \set{\G'_x}_{x \in P} \) is a \( P \)\nbd matching family in \( C \).
    Since \( C \) is stricter, it admits an amalgamation \( \G' \colon \molecin{P} \to C \). 
    Post-composing \( \G' \) with the unit \( \unit_C \colon C \to \trunc{n}(C) \), we obtain the strict functor \( \unit_C \after \G' \), which is the candidate amalgamation \( \G \) by Lemma \ref{lem:strict_functor_determined_by_basis}.
    This shows that \( \trunc{n}(C) \) is stricter, and concludes the proof.
\end{proof}

\begin{dfn}[\( n \)\nbd skeleton and \( n \)\nbd truncation]
    Let \( n \geq 0 \) and \( C \) be a stricter \( n \)\nbd category.
    The \emph{\( n \)\nbd skeleton} of \( C \) is the stricter \( n \)\nbd category \( \skel{n}(C) \).
    The \emph{\( n \)\nbd truncation} of \( C \) is the stricter \( n \)\nbd category \( \trunc{n}(C) \).
\end{dfn}

\noindent The adjoint triple \( \trunc{n} \dashv \iota_n \dashv \skel{n} \) restricts the adjoint triple
\begin{center}
    \begin{tikzcd}
        {\snCat{n}} && \somegaCat.
        \arrow["{\iota_n}"{description}, from=1-1, to=1-3]
        \arrow["{\skel{n}}", shift left=2, curve={height=-12pt}, from=1-3, to=1-1]
        \arrow["{\trunc{n}}"', shift right=2, curve={height=12pt}, from=1-3, to=1-1]
    \end{tikzcd}
\end{center}
Notice that given a stricter \( \omega \)\nbd category \( C \), we have a chain of inclusions 
\begin{equation*}
    \skel{-1} C \incl \skel{0} C \incl \skel{1} C \incl \ldots \incl \skel{n} C \incl \ldots
\end{equation*}
whose colimit \( \somegaCat \) is \( C \).

The following definition is adapted from \cite[8.2.1]{hadzihasanovic2024combinatorics}.
\begin{dfn} [Cellular extension] \label{dfn:cellular_extension}
    Let \( C \) be a stricter \( \omega \)\nbd category.
    A \emph{cellular extension of \( C \)} is a stricter \( \omega \)\nbd category \( C_{\cls{S}} \) together with a pushout diagram 
    \begin{center}
        \begin{tikzcd}[column sep=large]
            {\coprod_{e \in \cls{S}} \bd{}{}U_e} & {\coprod_{e \in \cls{S}} \molecin{U_e}} \\
            C & {C_{\cls{S}}}
            \arrow[""{name=0, anchor=center, inner sep=0}, "{\molecin{\bd{e}{}}}", from=1-1, to=1-2]
            \arrow["{(\bd{}{}e)_{e \in \cls{S}}}"', from=1-1, to=2-1]
            \arrow["{(e)_{e \in \cls{S}}}", from=1-2, to=2-2]
            \arrow[from=2-1, to=2-2]
            \arrow["\lrcorner"{anchor=center, pos=0.125, rotate=180}, draw=none, from=2-2, to=0]
        \end{tikzcd}
    \end{center}
    in \( \somegaCat \), where, for each \( e \in \cls{S} \), \( U_e \) is an atom.
\end{dfn}

\begin{comm}  \label{comm:def_cellular_extension}
    This is a non-standard definition of cellular extension, which is a priori more general than the usual one, that would require each of the atoms \( U_e \) to be globes.
    However, by Corollary \ref{cor:pushout_principal_cell} applied to the unique subdivision \( s \colon \dglobe{{\dim U}} \sd U \), we may turn every cellular extension in our sense into one in the restricted sense. 
    See \cite[Comment 8.2.2]{hadzihasanovic2024combinatorics}. 
\end{comm}

\begin{dfn} [Generalised substitution]
    Let \( U, V, P \) be regular directed complexes, \( s \colon U \sd V \) be a subdivision with formal dual \( c \), and \( \iota \colon U \incl P \) be an inclusion.
    The \emph{generalised substitution of \( U \) for \( V \) in \( P \)} is the oriented graded poset \( \subs{P}{V}{U}_s \) whose underlying set is \( (P \setminus \iota(U)) \coprod V \), with partial order defined for each \( z \in \subs{P}{V}{U}_s  \) and \( \a \in \set{-, +} \), by
    \begin{equation*}
        \cofaces{}{\a} z \eqdef 
        \begin{cases}
            \cofaces{P}{\a} z, & \text{if } z \in P \setminus \iota(U), \\
            \cofaces{V}{\a} z + \cup \set{\cofaces{P}{\a} y \mid y = \iota(c(z)), \dim y = \dim z} & \text{if } z \in V.
        \end{cases}
    \end{equation*}
    This comes equipped with the following commutative square in \( \Pos \)
    \begin{center}
        \begin{tikzcd}
            U & P \\
            V & {{\subs P V U}_s.}
            \arrow["\iota", hook, from=1-1, to=1-2]
            \arrow["c", from=2-1, to=1-1]
            \arrow["{\iota'}"', hook, from=2-1, to=2-2]
            \arrow["{c'}"', from=2-2, to=1-2]
        \end{tikzcd}
    \end{center}
\end{dfn}

\begin{lem} \label{lem:generalised_substitution}
    Let \( U, V, P \) be regular directed complexes, \( s \colon U \sd V \) be a subdivision with formal dual \( c \), and \( \iota \colon U \incl P \) be an inclusion.
    Then \( \subs{P}{V}{U}_s \) is a regular directed complex, the formal dual of \( c' \colon \subs{P}{V}{U}_s \to P \) is a subdivision \( s' \), and the square of strict functors
    \begin{center}
        \begin{tikzcd}
            {\molecin{U}} & {\molecin{P}} \\
            {\molecin{V}} & {\molecin{({\subs P V U}_s)}}
            \arrow[""{name=0, anchor=center, inner sep=0}, "{{{\molecin{\iota}}}}", from=1-1, to=1-2]
            \arrow["{{{\molecin{s}}}}"', from=1-1, to=2-1]
            \arrow["{{{\molecin{s'}}}}", from=1-2, to=2-2]
            \arrow["{\molecin{\iota'}}"', from=2-1, to=2-2]
            \arrow["\lrcorner"{anchor=center, pos=0.125, rotate=180}, draw=none, from=2-2, to=0]
        \end{tikzcd}
    \end{center}
    is a pushout in \( \somegaCat \).
\end{lem}
\begin{proof}
    That \( \subs{P}{V}{U}_s \) is a regular directed complex and \( s' \colon P \sd \subs{P}{V}{U}_s \) is a subdivision follows from \cite[Proposition 1.46, Comment 1.48]{chanavat2025semistrict}.
    We prove that the square is a pushout.
    Consider a stricter \( \omega \)\nbd category \( C \), together with strict functors \( \F \colon \molecin{P} \to C \) and \( \G \colon \molecin{V} \to C \) such that \( \F \after \molecin{\iota} = \G \after \molecin{s} \).
    Let \( \set{\F_x}_{x \in P} \) and \( \set{\G_x}_{x \in V} \) be respectively the matching families that \( \F \) and \( \G \) are the amalgamation of.
    For each \( x \in {\subs P V U}_s \), we let 
    \begin{equation} \label{eq:H_matching_of}
        \fun{H}_x \eqdef 
        \begin{cases}
            \F_x & \text{if } x \in V \\
            \G_x & \text{else}.
        \end{cases}
    \end{equation}
    By construction, \( \set{\fun{H}_x}_{x \in {\subs P V U}_s} \) is a matching family in \( C \).
    Since \( C \) is stricter, it has an amalgamation \( \fun{H} \colon \molecin{({\subs P V U}_s)} \to C \).
    By Lemma \ref{lem:strict_functor_determined_by_basis}, \( \fun{H} \after \molecin{\iota'} = \F \) and \( \fun{H} \after \molecin{s'} = \G \).
    Any other strict functor \( \fun{H}' \) with this property is necessarily the amalgamation of the same matching family.
    By Lemma \ref{lem:at_most_one_lift}, this proves uniqueness and concludes the proof. 
\end{proof}

\begin{cor} \label{cor:pushout_principal_cell}
    Let \( s \colon U \sd V \) be a subdivision between atoms.
    Then the square
    \begin{center}
        \begin{tikzcd}
            {\molecin{(\bd{}{}U)}} & {\molecin{U}} \\
            {\molecin{(\bd{}{}V)}} & {\molecin{V}}
            \arrow[from=1-1, to=1-2]
            \arrow["{\molecin{(\restr{s}{\bd{}{}U})}}"', from=1-1, to=2-1]
            \arrow["{\molecin{s}}", from=1-2, to=2-2]
            \arrow[from=2-1, to=2-2]
        \end{tikzcd}
    \end{center}
    is a pushout square in \( \somegaCat \).
\end{cor}
\begin{proof}
    By Lemma \ref{lem:generalised_substitution}.
\end{proof}

\begin{dfn} [Stricter polygraph] \label{dfn:stricter_polygraph}
    A \emph{stricter polygraph} is a stricter \( \omega \)\nbd category \( C \), together with, for each \( n \geq 0 \), a pushout diagram
    \begin{center}
        \begin{tikzcd}[column sep=large]
            {\coprod_{e \in \cls{S}_n} \bd{}{}U_e} & {\coprod_{e \in \cls{S}_n} \molecin{U_e}} \\
            \skel{n - 1}C & {\skel{n} C}
            \arrow[""{name=0, anchor=center, inner sep=0}, "{\molecin{\bd{e}{}}}", from=1-1, to=1-2]
            \arrow["{(\bd{}{}e)_{e \in \cls{S}_n}}"', from=1-1, to=2-1]
            \arrow["{(e)_{e \in \cls{S}_n}}", from=1-2, to=2-2]
            \arrow[from=2-1, to=2-2]
            \arrow["\lrcorner"{anchor=center, pos=0.125, rotate=180}, draw=none, from=2-2, to=0]
        \end{tikzcd}
    \end{center}
    in \( \somegaCat \), exhibiting \( \skel{n}C \) as a cellular extension of \( \skel{n - 1}C \), and such that for each \( e \in \cls{S}_n \), \( \dim e = n \).
    The set \( \cls{S} = \coprod_{k \geq 0} \cls{S}_k \) is called the \emph{generating set of globular cells} of \( C \).
    More generally, we say that a strict functor \( \F \colon A \to C \) of composition structure is a \emph{relative stricter polygraph} if \( \F \) can be obtained as the transfinite composition of cellular extensions of \( A \).
\end{dfn}

\begin{lem} \label{lem:stricter_polygraph_basis}
    Let \( (C, \cls{S}) \) be a stricter polygraph.
    Then the set \( \cls{S} \) is a basis for \( C \).
\end{lem}
\begin{proof}
    The proof is similar to the case of polygraphs, see \cite[Proposition 15.1.8, Lemma 16.6.2]{ara2025polygraphs}.
\end{proof}

\begin{lem} \label{lem:stricter_regular_complex_are_stricter_polygraph}
    Let \( P \) be a regular direct complex.
    Then \( \molecin{P} \) is a stricter polygraph.
\end{lem}
\begin{proof}
    By Corollary \ref{cor:molecin_preserves_pushout_inclusions}, the square
    \begin{center}
        \begin{tikzcd}
            {\coprod_{x \in \gr{n}P} \molecin{\bd{}{}\imel P x}} & {\coprod_{x \in \gr{n}P} \molecin{\imel P x}} \\
            {\skel{n - 1}P} & {\skel{n} P}
            \arrow["{{\molecin{\bd{e}{}}}}", from=1-1, to=1-2]
            \arrow["{{(\bd{}{}\molecin{\mapel x})_{x \in \gr n P}}}"', from=1-1, to=2-1]
            \arrow["{{(\molecin{\mapel x})_{x \in \gr n P}}}", from=1-2, to=2-2]
            \arrow[from=2-1, to=2-2]
        \end{tikzcd}
    \end{center}
    is a pushout in \( \somegaCat \).
    This concludes the proof.
\end{proof}

\noindent We conclude this section by describing \( \somegaCat \) as a subcategory of a category of presheaves.

\begin{dfn}
    We let \( \omegaReg \) be the full subcategory of \( \somegaCat \) on stricter \( \omega \)\nbd categories of the form \( \molecin{P} \), for \( P \) a \emph{finite} regular directed complex.
\end{dfn}

\begin{comm}
    The finiteness condition is only here to ensure that \( \omegaReg \) is a small category. 
\end{comm}

\begin{dfn} [Rewrite and pasting condition] \label{dfn:rewrite_condition}
    Let \( X \colon \opp{\omegaReg} \to \Set \) be a presheaf. 
    We say that \( X \) satisfies \emph{the rewrite condition} if for all atoms \( U \) of dimension \( n \in \mathbb{N} \), letting \( s \colon \dglobe{n} \sd U \) be the unique subdivision, \( X \) sends the square
    \begin{center}
        \begin{tikzcd}
            {\molecin{(\bd{}{}\dglobe{n})}} & {\molecin{\dglobe{n}}} \\
            {\molecin{(\bd{}{}U)}} & {\molecin{U}}
            \arrow[""{name=0, anchor=center, inner sep=0}, from=1-1, to=1-2]
            \arrow["{{\molecin{(\restr{s}{\bd{}{}\dglobe{n}})}}}"', from=1-1, to=2-1]
            \arrow["{{\molecin{s}}}", from=1-2, to=2-2]
            \arrow[from=2-1, to=2-2]
        \end{tikzcd}
    \end{center}
    to a pullback square.
    We say that \( X \) satisfies the \emph{pasting condition} if for all finite regular directed complex \( P \), \( X \) sends the cone 
    \begin{equation*}
        \set{\molecin{\imel{P}{x}} \to \molecin{P}}_{x \in P}
    \end{equation*}
    over \( \molecin{P} \) to a limit cone.
    We let \( \omegaRegSet \) be the full subcategory of \( [\opp{\omegaReg}, \Set] \) on presheaves satisfying the rewrite and pasting conditions.
\end{dfn}

\begin{rmk}
    Let \( X \colon \opp{\omegaReg} \to \Set \) be a presheaf, and \( P \) a finite regular directed complex. 
    We may still call a cone \( \set{t_x \colon \molecin{\imel{P}{x}} \to X}_{x \in P} \) a \( P \)\nbd matching family in \( X \), and an extension along \( s_P \) an amalgamation.
    Then \( X \) satisfies the pasting condition if for all finite regular directed complexes \( P \), all \( P \)\nbd matching families in \( X \) have a unique amalgamation.
\end{rmk}

\begin{dfn}
    Let \( X \colon \opp{\omegaReg} \to \Set \) be a presheaf, \( U \) be a molecule of dimension \( n \geq 0 \), and \( t \colon \molecin{U} \to X \) a natural transformation.
    Then there exists a unique strict functor \( \F \colon \molecin{\dglobe{n}} \to \molecin{U} \) classifying \( \idd{U} \).
    The \emph{principal cell of \( t \)} is the natural transformation \( \pcell{t} \eqdef t \after \F \colon \molecin{\dglobe{n}} \to X \).
\end{dfn}

\begin{dfn}
    Let \( X \colon \opp{\omegaReg} \to \Set \) be a presheaf satisfying the rewrite and pasting conditions.
    The \emph{composition structure associated to \( X \)} is the composition structure \( \phi(X) \eqdef \coprod_{n \geq 0} X(\dglobe{n}) \), whose boundary operators are induced, for all \( k \in \mathbb{N} \) and \( \a \in \set{- ,+} \), by the strict functors
    \begin{equation*}
        \bd{k}{\a} \colon \molecin{\dglobe{k}} \to \molecin{\dglobe{n}}, 
    \end{equation*}
    and \( k \)\nbd composition operation is induced by the strict functor
    \begin{equation*}
        \molecin{\dglobe{n}} \to \molecin{(\dglobe{n} \cp{k} \dglobe{n})},
    \end{equation*}
    classifying \( \idd{(\dglobe{n} \cp{k} \dglobe{n})} \).
    This construction extends to a functor 
    \begin{equation*}
        \phi \colon \omegaRegSet \to \Comp.
    \end{equation*}
\end{dfn}

\begin{lem} \label{lem:stricter_hom_set_iso_presheaf}
    Let \( X \colon \opp{\omegaReg} \to \Set \) be a presheaf satisfying the rewrite and pasting conditions, and \( P \) be a finite regular directed complex.
    Then there is a bijection
    \begin{equation*}
        X(\molecin{P}) \cong \Comp(\molecin{P}, \phi(X)),
    \end{equation*}
    natural in \( X \) and \( U \).
\end{lem}
\begin{proof}
    Let \( t \in X(\molecin{P}) \), which by the Yoneda Lemma, is a natural transformation \( t \colon \molecin{P} \to X \).
    We define \( \F \colon \molecin{P} \to \phi(X) \) by sending \( w \) in \( \molecin{P} \) to \( \pcell{t \after \molecin{w}} \), which is, by definition of \( \phi(X) \), a strict functor of composition structures.
    Conversely, let \( \F \colon \molecin{P} \to \phi(X) \) be a strict functor, and let \( \set{\F_x}_{x \in P} \) be the matching family of which it is the amalgamation.
    We construct by induction on \( n \), a matching family \( \set{t_x \colon \molecin{\imel{P}{x}} \to X}_{x \in \gr{\le n}{P}} \) such that \( \pcell{t_x} = \pcell{\F_x} \).    
    For \( x \in \gr{0}{P} \), we let \( t_x \colon \molecin{\pt} \to X \) classifying \( \pcell{\F_x} \in X(\globe{0}) \).
    Let \( n > 0 \) and suppose inductively that the matching family is constructed for all \( x \in \gr{< n}{P} \).
    Let \( x \in \gr{n}{P} \) and let \( s \colon \dglobe{n} \sd \imel{P}{x} \) be the unique subdivision.
    Then we have a commutative diagram
    \begin{center}
        \begin{tikzcd}
            {\molecin{(\bd{}{}\dglobe{n})}} & {\molecin{\dglobe{n}}} \\
            {\molecin{(\bd{}{}\imel{P}{x})}} & X
            \arrow[from=1-1, to=1-2]
            \arrow["{{\molecin{(\restr{s}{\bd{}{}\dglobe{n}})}}}"', from=1-1, to=2-1]
            \arrow["{\pcell{\F_x}}", from=1-2, to=2-2]
            \arrow["{t_{\bd{}{} \imel{P}{x}}}"', from=2-1, to=2-2]
        \end{tikzcd}
    \end{center}
    where \( t_{\bd{}{} \imel{P}{x}} \) is the amalgamation of \( \set{t_y \colon \molecin{\imel{P}{y}} \to X}_{y \in \bd{}{} \imel{P}{x}} \).
    Since \( X \) satisfies the rewrite condition, this data defines a unique natural transformation \( t_x \colon \molecin{\imel{P}{x}} \to X \) such that \( t_x \after \molecin{s} = \pcell{\F_x} \).
    This concludes the construction of the matching family.
    Since \( X \) satisfies the pasting condition, the matching family admits an amalgamation \( t \colon \molecin{P} \to X \), defining the desired element of \( X(\molecin{P}) \).
    It is straightforward to check naturality and that those two constructions are inverse of each other.
\end{proof}

\begin{prop} \label{prop:stricter_cat_are_local_presheaves}
    The categories \( \omegaRegSet \) and \( \somegaCat \) are equivalent, realised by the functors \( X \mapsto \phi(X) \) and \( C \mapsto \somegaCat(\molecin{-}, C) \). 
\end{prop}
\begin{proof}
    For all presheaves \( X \) in \( \omegaRegSet \), we claim that \( \phi(X) \) is a stricter \( \omega \)\nbd category.
    Indeed, a \( P \)\nbd matching family \( \set{\F_x \colon \molecin{\imel{P}{x}} \to \phi(X)}_{x \in P} \) defines, by Lemma \ref{lem:stricter_hom_set_iso_presheaf} a matching family \( \set{t_x \colon \molecin{\imel{P}{x}} \to X} \) which has an amalgamation \( t \colon \molecin{P} \to X \), which, by Lemma \ref{lem:stricter_hom_set_iso_presheaf} again, defines a strict functor \( \F \colon \molecin{P} \to \phi(X) \), which is the amalgamation of \( \set{\F_x}_{x \in P} \). 
    Thus \( X \mapsto \phi(X) \) defines a functor \( \omegaRegSet \to \somegaCat \).
    We construct an inverse up to natural isomorphism to \( \phi \).
    Let \( C \) be a stricter \( \omega \)\nbd category.
    Then the presheaf defined by \(\molecin{P} \mapsto \somegaCat(\molecin{P}, C) \) is \( S \)\nbd local by definition, and satisfy the rewrite condition by Corollary \ref{cor:pushout_principal_cell}.
    This defines a functor \( \psi \colon \somegaCat \to \omegaRegSet \).
    One sees directly that \( \phi \after \psi \) is isomorphic to the identity on \( \somegaCat \). 
    By Lemma \ref{lem:stricter_hom_set_iso_presheaf}, it is also the case of \( \psi \after \phi \).
    This concludes the proof.
\end{proof}

\subsection{Gray product of stricter \texorpdfstring{$\omega$}{ω}-categories}

Recall that if \( P, Q \) are regular directed complexes, the basis \( \atomin{(P \gray Q)} \) of \( \molecin{(P \gray Q)} \) is given exactly by the local embeddings \( u \gray v \) for \( u \in \atomin{P} \) and \( v \in \atomin{Q} \).  

\begin{dfn} [Gray product] \label{dfn:gray_product_of_stricter_regular_complexes}
    Let \( P, Q \) be regular directed complexes.
    The \emph{Gray product} of \( \molecin{P} \) and \( \molecin{Q} \) is the stricter \( \omega \)\nbd category
    \begin{equation*}
        \molecin{P} \gray \molecin{Q} \eqdef \molecin{(P \gray Q)}.
    \end{equation*}
    If \( \F \colon \molecin{P} \to \molecin{P'} \) and \( \G \colon \molecin{Q} \to \molecin{P'} \) are two strict functors, we let 
    \begin{equation*}
        \F \gray \G \colon \atomin{P} \times \atomin{Q} \to  \molecin{P'} \gray \molecin{Q'}
    \end{equation*}
    defined by sending a pair \( (u, v) \) to \( \F(u) \gray \G(v) \).
\end{dfn}

\begin{lem} \label{lem:gray_of_strict_functors}
    Let \( \F \colon \molecin{P} \to \molecin{P'} \) and \( \G \colon \molecin{Q} \to \molecin{P'} \) be strict functors. 
    Then \( \F \gray \G \) extends uniquely to a strict functor 
    \begin{equation*}
        \F \gray \G \colon \molecin{P} \gray \molecin{Q} \to \molecin{P'} \gray \molecin{Q'}.
    \end{equation*}
\end{lem}
\begin{proof}
    Suppose that \( \F \) and \( \G \) are given by the matching families \( \set{\F_x}_{x \in P} \) and \( \set{\G_y}_{y \in Q} \) respectively.
    We show by induction on \( n \) that the data of \( \set{\pcell{\F_x} \gray \pcell{\G_y}}_{\dim (x, y) \le n} \) determines, as per Remark \ref{rmk:data_matching family}, a \( (\gr{\le n}{(P \gray Q)}) \)\nbd matching family in \( \molecin{(P' \gray Q')} \).
    When \( n = 0 \), the statement is clear. 
    Inductively, let \( n > 0 \) and let \( (x, y) \in P \gray Q \) of dimension \( n \). 
    Then by inductive hypothesis, \( \set{\F_{x'} \gray G_{y'}}_{(x', y') < (x, y)} \) forms a \( \bd{}{} (x, y) \)\nbd matching family in \( \molecin{(P' \gray Q')} \).
    By Proposition \ref{prop:regular_directed_complex_stricter}, this matching family has an amalgamation \( \bd{}{}\fun{H} \colon \molecin{(\bd{}{} (x, y))} \to \molecin{(P' \gray Q')} \).
    We show that \( \bd{}{} \fun{H} \) extends to a strict functor \( \fun{H} \colon \molecin{\clset{(x, y)}} \to \molecin{(P' \gray Q')} \) by sending the principal cell to \( \pcell{\F_x} \gray \pcell{\G_y} \).
    For \( k \in \mathbb{N} \) and \( \a \in \set{-, +} \), we have
    \begin{align*}
        \bd{k}{\a} (\pcell{\F_x} \gray \pcell{\G_y}) &= \bigcup_{i = 1}^k \bd{i}{\a} \pcell{\F_x} \gray \bd{k - i}{(-)^i\a} \pcell{\G_y} \\
                                       &= \bigcup_{i = 1}^k \pcell{\bd{i}{\a} \F_x} \gray \pcell{\bd{k - i}{(-)^i\a} \G_y} \\
                                       &= \fun{H}(\bd{k}{\a} \idd{(x, y)}).
    \end{align*}
    Thus, \( \fun{H} \) is a morphism of the underlying globular graph, and since \( \idd{(x, y)} \) is the only globular cell of dimension \( \dim (x, y) \) in \( \molecin{(\clset{(x, y)})} \), this is enough to conclude that \( \fun{H} \) is a strict functor.
    This concludes the induction and shows that \( \set{\pcell{\F_x} \gray \pcell{\G_y}}_{(x, y) \in P \gray Q} \) determines a matching family in \( \molecin{(P' \gray Q')} \).
    By Proposition \ref{prop:regular_directed_complex_stricter}, this matching family has an amalgamation \( \F \gray \G \).
    Uniqueness is given by Lemma \ref{lem:strict_functor_determined_by_basis}.
    This concludes the proof.
\end{proof}

\begin{cor} \label{cor:gray_prodcut_omegareg_monoidal}
    The Gray product determines a monoidal structure on the category \( \omegaReg \), whose monoidal unit is the terminal stricter \( \omega \)\nbd category \( \globe{0} \).
\end{cor}
\begin{proof}
    Lemma \ref{lem:gray_of_strict_functors} shows that \( - \gray - \) is well-defined on strict functors. 
    Since for all regular directed complexes \( P \), \( \pt \gray P = P = P \gray \pt \), we deduce that the monoidal unit is \( \molecin{\pt} = \globe{0} \).
    Functoriality is straightforward.
    This concludes the proof.
\end{proof}

\begin{rmk}
    If \( \F \colon \molecin{P} \to \molecin{P'} \) and \( \G \colon \molecin{Q} \to \molecin{P'} \) are strict functors, \( u \in \molecin{P} \), and \( v \in \molecin{Q} \), then 
    \begin{equation*}
       (\F \gray \G)(u \gray v) = \F(u) \gray \G(v). 
    \end{equation*}
\end{rmk}

\begin{lem} \label{lem:rewrite_condition_for_gray}
    Let \( P \) be a regular directed complex, and \( s \colon U \sd V \) be a subdivision between atoms.
    Then the square
    \begin{center}
        \begin{tikzcd}
            {\molecin{(P \gray \bd{}{}U)}} & {\molecin{(P \gray U)}} \\
            {\molecin{(P \gray \bd{}{}V)}} & {\molecin{(P \gray V)}}
            \arrow[from=1-1, to=1-2]
            \arrow["{\molecin{(\restr{P \gray s}{\bd{}{}U})}}"', from=1-1, to=2-1]
            \arrow["{{\molecin{P \gray s}}}", from=1-2, to=2-2]
            \arrow[from=2-1, to=2-2]
        \end{tikzcd}
    \end{center}
    is a pushout square in \( \somegaCat \).
\end{lem}
\begin{proof}
    By construction, \( P \gray V \) is the generalised substitution of \( P \gray (\bd{}{} U) \) for \( P \gray (\bd{}{} V) \) in \( P \gray U \).
    We conclude by Lemma \ref{lem:generalised_substitution}.
\end{proof}

\begin{dfn} 
    Let \( P \) be a regular directed complex and \( C \) be a stricter \( \omega \)\nbd category.
    By \cite[Lemma 7.2.8]{hadzihasanovic2024combinatorics} and Lemma \ref{lem:rewrite_condition_for_gray}, the presheaf on \( \omegaReg \) given by
    \begin{equation*}
        \molecin{U} \mapsto \somegaCat(\molecin{(P \gray U)}, C) 
    \end{equation*}
    satisfies the rewrite and pasting conditions.
    By Proposition \ref{prop:stricter_cat_are_local_presheaves}, this defines the stricter \( \omega \)\nbd category 
    \begin{equation*}
        \homlax(\molecin{P}, C),
    \end{equation*}
    whose globular \( n \)\nbd cells are strict functors \( \F \colon \molecin{(P \gray \dglobe{n})} \to C \).
    Dually, we can also define the stricter \( \omega \)\nbd category
    \begin{equation*}
        \homcolax(\molecin{P}, C),
    \end{equation*}
    whose globular \( n \)\nbd cells are strict functors \( \F \colon \molecin{(\dglobe{n} \gray P)} \to C \).
\end{dfn}

\begin{lem}
    Let \( P, Q \) be finite regular directed complexes and \( C \) be a stricter \( \omega \)\nbd category.
    Then there are bijections
    \begin{align*}
        \somegaCat(\molecin{(P \gray Q)}, C) &\cong \somegaCat(\molecin{P}, \homcolax(\molecin{Q}, C)) \\
                                             &\cong \somegaCat(\molecin{Q}, \homlax(\molecin{P}, C)),
    \end{align*}
    natural in \( \molecin{P}, \molecin{Q} \) and \( C \).
\end{lem}
\begin{proof}
    Follows directly by Proposition \ref{prop:stricter_cat_are_local_presheaves}.
\end{proof}

\noindent Applying \cite[Th\'eor\`eme 5.3]{ara2020joint} together with the previous result, we get the following definition.
\begin{dfn} [Gray product of stricter \( \omega \)\nbd categories] \label{dfn:gray_product_stricter_categories} 
    Let \( C, D \) be stricter \( \omega \)\nbd categories.
    The Gray product of \( C \) and \( D \) is the stricter \( \omega \)\nbd category
    \begin{equation*}
        \colim_{\substack{u \in \molecin{P} \to C \\ v \in\molecin{Q} \to D}} \molecin{(P \gray Q)},
    \end{equation*}
    where \( P \) and \( Q \) are finite regular directed complexes.
    This determines a biclosed monoidal structure on \( \somegaCat \) whose monoidal unit is the terminal stricter \( \omega \)\nbd category \( \globe{0} \) and such that the inclusion \( \omegaReg \incl \somegaCat \) is strong monoidal.
\end{dfn}

\begin{rmk}
    Let \( P, Q \) be regular directed complexes.
    Since \( - \gray - \) is biclosed and using Corollary \ref{cor:regular_directed_complex_colimit_of_itself}, we get
    \begin{align*}
        \molecin{P} \gray \molecin{Q} &\cong \colim_{x \in P, y \in Q} \molecin{\imel{P}{x}} \gray \molecin{\imel{Q}{y}} \\
                                      &\cong \colim_{(x, y) \in P \gray Q} \molecin{(\imel{P}{x} \gray \imel{Q}{y})} \\
                                      &= \molecin{(P \gray Q)}.
    \end{align*}
    Thus Definition \ref{dfn:gray_product_of_stricter_regular_complexes} and Definition \ref{dfn:gray_product_stricter_categories} agree for not necessarily finite regular directed complexes.
\end{rmk}

\subsection{Strict and stricter categories}

The goal of this section is to clarify the relationship between strict and stricter categories.

\begin{dfn} [Theta]
    Let \( U \) be a molecule.
    We say that \( U \) is a \emph{theta} if for all \( x \in U \), \( \clset{x} \) is a globe.
    We write \( \Theta \) for the full subcategory of \( \omegaReg \) on \( \molecin{U} \), for \( U \) a theta.
\end{dfn}

\begin{rmk} \label{rmk:theta_is_theta}
    By \cite[Corollary 9.1.29]{hadzihasanovic2024combinatorics}, a molecule is a theta if and only if it is a pasting of globes.
    Therefore, by \cite[Theorem 8.2.14, Lemma 9.1.16]{hadzihasanovic2024combinatorics}, the category \( \Theta \) is isomorphic to Joyal's \( \Theta \)\nbd category, the full subcategory of the category of strict \( \omega \)\nbd categories on pastings of globes.  
\end{rmk}

\begin{dfn} [Strict \( \omega \)\nbd category]
    We define \( S^\Theta \) to be the subset of \( S \) defined by 
    \begin{equation*}
        S^\Theta \eqdef \set{s_U \colon \colim_{x \in U} \molecin{\imel{U}{x}} \to \molecin{U} \mid U \text{ a theta}}.
    \end{equation*}  
    A \emph{strict \( \omega \)\nbd category} is a composition structure \( C \) which is local with respect to \( S^\Theta \).
    We write \( \omegaCat \) for the category of strict \( \omega \)\nbd categories and strict functors.
\end{dfn}

\begin{rmk}
    By \cite[Theorem 1.12]{berger2002cellular}, this definition is equivalent to the standard definition.
\end{rmk}

\begin{prop} \label{prop:stricter_are_strict}
    Let \( C \) be a stricter \( \omega \)\nbd category.
    Then \( C \) is a strict \( \omega \)\nbd category.
\end{prop}
\begin{proof}
    Since \( C \) is local with respect to \( S \), it is in particular local with respect to \( S^\Theta \subseteq S \).
\end{proof} 

\noindent Akin to stricter \( \omega \)\nbd categories, strict \( \omega \)\nbd categories are a reflective subcategory of \( \Comp \).
By Proposition \ref{prop:stricter_are_strict}, we have a sequence of full subcategory inclusions
\begin{equation*}
     \somegaCat \incl \omegaCat \incl \Comp.
\end{equation*}
We define
\begin{equation*}
    \rcs \colon \omegaCat \to \somegaCat
\end{equation*}
to be the functor applying the reflector \( \rc \colon \Comp \to \somegaCat  \) to the underlying composition structure of a strict \( \omega \)\nbd category.
The functor \( \rcs \) is left adjoint and exhibits \( \somegaCat \) as a reflective subcategory of \( \omegaCat \).

\begin{dfn} [Strict \( n \)\nbd categories]
    Let \( n \in \mathbb{N} \).
    A \emph{strict \( n \)\nbd category} is a strict \( \omega \)\nbd category which is also an \( n \)\nbd composition structure.
    We write \( \nCat{n} \) for the full subcategory of \( \omegaCat \) on strict \( n \)\nbd categories.
\end{dfn}

\begin{rmk}
    If \( C \) is a strict \( n \)\nbd category, then the stricter \( \omega \)\nbd category \( \rcs C \) is a stricter \( n \)\nbd category.
\end{rmk}

\noindent As in the case of stricter \( \omega \)\nbd categories, we have \( n \)\nbd skeleton and \( n \)\nbd truncation functors \( \skel{n}, \trunc{n} \colon \omegaCat \to \nCat{n} \) fitting in a commutative diagram
\begin{center}
    \begin{tikzcd}
        {\nCat n} & \omegaCat \\
        {\snCat n} & \somegaCat.
        \arrow[""{name=0, anchor=center, inner sep=0}, hook, from=1-1, to=1-2]
        \arrow[""{name=1, anchor=center, inner sep=0}, "\rcs"', shift right=2, from=1-1, to=2-1]
        \arrow[""{name=2, anchor=center, inner sep=0}, "{\trunc n}"', shift right=3, from=1-2, to=1-1]
        \arrow[""{name=3, anchor=center, inner sep=0}, "{\skel n}", shift left=3, from=1-2, to=1-1]
        \arrow[""{name=4, anchor=center, inner sep=0}, "\rcs"', shift right=2, from=1-2, to=2-2]
        \arrow[""{name=5, anchor=center, inner sep=0}, shift right=2, hook, from=2-1, to=1-1]
        \arrow[""{name=6, anchor=center, inner sep=0}, hook, from=2-1, to=2-2]
        \arrow[""{name=7, anchor=center, inner sep=0}, shift right=2, hook, from=2-2, to=1-2]
        \arrow[""{name=8, anchor=center, inner sep=0}, "{\trunc n}"', shift right=3, from=2-2, to=2-1]
        \arrow[""{name=9, anchor=center, inner sep=0}, "{\skel n}", shift left=3, from=2-2, to=2-1]
        \arrow["\dashv"{anchor=center}, draw=none, from=1, to=5]
        \arrow["\dashv"{anchor=center, rotate=-90}, draw=none, from=0, to=3]
        \arrow["\dashv"{anchor=center}, draw=none, from=4, to=7]
        \arrow["\dashv"{anchor=center, rotate=-90}, draw=none, from=2, to=0]
        \arrow["\dashv"{anchor=center, rotate=-90}, draw=none, from=6, to=9]
        \arrow["\dashv"{anchor=center, rotate=-90}, draw=none, from=8, to=6]
    \end{tikzcd}
\end{center}

\begin{dfn} [Polygraph]
    A \emph{polygraph} is a strict \( \omega \)\nbd category \( C \), together with, for each \( n \geq 0 \), a pushout diagram
    \begin{center}
        \begin{tikzcd}[column sep=large]
            {\coprod_{e \in \cls{S}_n} \bd{}{}U_e} & {\coprod_{e \in \cls{S}_n} \molecin{U_e}} \\
            \skel{n - 1}C & {\skel{n} C}
            \arrow[""{name=0, anchor=center, inner sep=0}, "{\molecin{\bd{e}{}}}", from=1-1, to=1-2]
            \arrow["{(\bd{}{}e)_{e \in \cls{S}_n}}"', from=1-1, to=2-1]
            \arrow["{(e)_{e \in \cls{S}_n}}", from=1-2, to=2-2]
            \arrow[from=2-1, to=2-2]
            \arrow["\lrcorner"{anchor=center, pos=0.125, rotate=180}, draw=none, from=2-2, to=0]
        \end{tikzcd}
    \end{center}
    in \( \omegaCat \), exhibiting \( \skel{n}C \) as a cellular extension of \( \skel{n - 1}C \), and such that for each \( e \in \cls{S}_n \), \( \dim e = n \).
    The set \( \cls{S} = \coprod_{k \geq 0} \cls{S}_k \) is called the \emph{generating set} of \( C \).
    More generally, we say that a strict functor \( f \colon A \to C \) of composition structure is a \emph{relative polygraph} if \( f \) can be obtained as the transfinite composition of cellular extensions of \( A \).
\end{dfn}

\begin{rmk}
    This definition is equivalent to the usual definition of polygraphs, see again \cite[Comment 8.2.2]{hadzihasanovic2024combinatorics}.
\end{rmk}

\begin{lem} \label{lem:reflection_of_polygraphs_are_stricter_polygraphs}
    Let \( f \colon C \to D \) be a relative polygraph.
    Then \( \rcs f \) is a relative stricter polygraph.
\end{lem}
\begin{proof}
    Clear by Proposition \ref{prop:regular_directed_complex_stricter} and since \( \rcs \) is left adjoint.
\end{proof}

\noindent Next, recall from \cite[Appendice A]{ara2020joint} that strict \( \omega \)\nbd categories also support a Gray product --- our definition of Gray product of stricter \( \omega \)\nbd categories being adapted from it.

\begin{prop} \label{prop:reflection_to_stricter_monoidal}
    The functor \( \rcs \colon \omegaCat \to \somegaCat \) is strong monoidal with respect to the Gray product on stricter and strict \( \omega \)\nbd categories.
\end{prop}
\begin{proof}
    Since \( \rcs \) is left adjoint, and since \( \Theta \) are dense in \( \omegaCat \) by \cite[Proposition 4.6]{ara2020joint}, it is enough to show that for any two thetas \( U \) and \( V \), \( \molecin{(U \gray V)} \) and \( \rcs (\molecin{U} \gray \molecin{V}) \) are naturally isomorphic. 
    By \cite[Lemma 9.1.16]{hadzihasanovic2024combinatorics}, any theta is acyclic.
    This implies by \cite[Proposition 11.2.36]{hadzihasanovic2020diagrammatic} that \( \molecin{(U \gray V)} \cong \molecin{U} \gray \molecin{V} \) in \( \omegaCat \).
    Since \( \molecin{(U \gray V)} \) is stricter by Proposition \ref{prop:regular_directed_complex_stricter}, we conclude.
\end{proof}

\noindent We conclude this section by showing a partial converse to Proposition \ref{prop:stricter_are_strict}, and exhibiting a point of divergence between strict and stricter \( \omega \)\nbd categories.

\begin{thm}\label{thm:strict_le_3_are_stricter}
    Let \( n \le 3 \), and \( C \) be a strict \( n \)\nbd category.
    Then \( C \) is a stricter \( n \)\nbd category.
\end{thm}
\begin{proof}
    Let \( P \) be a regular directed complex with \( \dim P \le 3 \).
    By \cite[Corollary 8.4.12]{hadzihasanovic2024combinatorics}, \( \molecin{P} \) is a polygraph.
    Thus, the map
    \begin{equation*}
        s_P \colon \colim_{x \in P} \imel{P}{x} \to P 
    \end{equation*}
    is an isomorphism when computed in \( \omegaCat \).
    In particular, any strict \( n \)\nbd category \( C \) is local with respect to \( s_P \).
    By Lemma \ref{lem:stricter_n_iff_local_with_dim_le_n}, this concludes the proof.
\end{proof}

\begin{comm} \label{comm:strict_are_not_stricter}
    Thus, the category \( \nCat{n} \) and \( \snCat{n} \) are equivalent for \( n \le 3 \).
    However, they differ starting from \( n = 4 \).
    For instance, consider the \( 4 \)\nbd dimensional regular directed complex \( P \) of \cite[Example 8.2.20]{hadzihasanovic2024combinatorics}.
    Then \( \molecin{P} \) is \emph{not} a polygraph.
    Now, let \( Q \eqdef \colim_{x \in P} \molecin{\imel{P}{x}} \), where the colimit is computed in \( \omegaCat \).
    By construction and Theorem \ref{thm:strict_le_3_are_stricter}, \( Q \) is a polygraph, but it cannot be a stricter \( \omega \)\nbd category.
    Indeed, if it were the case, we would have \( \molecin{P} \cong \rcs Q \cong Q \), contradicting the fact that \( \molecin{P} \) is not a polygraph.
\end{comm}

\subsection{Suspension of stricter \texorpdfstring{$\omega$}{ω}-categories} \label{subsec:suspension}

\begin{dfn} 
    Let \( C \) be a composition structure with two objects \( a \) and \( b \).
    We define the composition structure
    \begin{equation*}
        C(a, b) \eqdef \set{u \in C \mid \bd{0}{-} u = a, \bd{0}{+} u = b},    
    \end{equation*}
    whose boundary operators and \( k \)\nbd composition are induced by the one of \( C \) shifted by \( 1 \).
\end{dfn}

\begin{lem} \label{lem:hom_of_stricter_is_stricter}
    Let \( C \) be a stricter \( \omega \)\nbd category with two objects \( a \) and \( b \).
    Then \( C(a, b) \) is a stricter \( \omega \)\nbd category.
\end{lem}
\begin{proof}
    Let \( U \) be a molecule.
    Any \( U \)\nbd matching family 
    \begin{equation*}
        \set{\F_x \colon \molecin{\imel{U}{x}} \to C(a, b)}_{x \in U}
    \end{equation*}
    determines a \( \sus{U} \)\nbd matching family in \( C \) by letting \( \F_{\sus{x}} \eqdef \F_x \) for \( x \in U \), and \( \F_{\bot^-}, \F_{\bot^+} \) be the strict functors from \( \molecin{\pt} \) classifying \( a \) and \( b \) respectively. 
    This matching family has an amalgamation \( \sus{\F} \colon \molecin{\sus{U}} \to C \), showing that the amalgamation of \( \set{\F_x}_{x \in U} \) is well-defined.
\end{proof}

\begin{comm}
    Thus, any stricter \( \omega \)\nbd category can canonically be seen as a category enriched in stricter \( \omega \)\nbd categories.
    The converse is not true. 
    Indeed, if it were the case, \( \snCat{4} \) would be equivalent to the categories of categories enriched in \( \snCat{3} \).
    Since \( \snCat{3} \) is equivalent to \( \nCat{3} \) by Theorem \ref{thm:strict_le_3_are_stricter}, this would mean that \( \snCat{4} \) is equivalent to \( \nCat{4} \).
    We know from Comment \ref{comm:strict_are_not_stricter} that this is not the case.
    We do not know any general condition guaranteeing that a category enriched in stricter \( \omega \)\nbd category is stricter.
\end{comm}

\begin{dfn} [Suspension]
    Let \( C \) be a composition structure.
    The \emph{suspension of \( C \)} is the composition structure \( \sus{C} \) with two objects \( \bot^+, \bot^- \) and such that
    \begin{equation*}
        \sus{C}(\bot^\a, \bot^\beta) \eqdef 
        \begin{cases}
            C       & \text{if } (\a, \beta) = (-, +),\\
            \set{*} & \text{if } \a = \beta,\\
            \varnothing & \text{else.}
        \end{cases}
    \end{equation*}
    The boundary operators and composition operations are induced by the one of \( C \). 
\end{dfn}

\noindent If \( C \) is a stricter \( \omega \)\nbd category, then \( \sus{C} \) is a strict \( \omega \)\nbd category, since it is the suspension of its underlying strict \( \omega \)\nbd category.
We conclude this section by showing that it is in fact a stricter \( \omega \)\nbd category. 

The following two definitions are adapted from \cite{chandler2019thin}.
\begin{dfn} [Diamond action]
    Let \( P \) be a finite thin graded poset, let \( x, y \in P \) such that \( x \le y \), \( \gamma \colon x \to \ldots \to y \) be a path from \( x \) to \( y \) in the covering diagram of \( P \), and \( D \eqdef \set{a < c_1, c_2 < b} \) be a diamond in \( P \), for two elements \( a, b \in P \) such that \( a \le b \) and \( \dim b - \dim a = 2 \).
    We define \( D\cdot \gamma \) to be the path
    \begin{equation*}
        D \cdot \gamma \eqdef 
        \begin{cases}
            (\gamma \setminus \set{c_1}) \cup \set{c_2} & \text{if } a \to c_1 \to b \text{ is a subpath of } \gamma, \\
            (\gamma \setminus \set{c_2}) \cup \set{c_1} & \text{if } a \to c_2 \to b \text{ is a subpath of } \gamma, \\
            \gamma & \text{else.}
        \end{cases}
    \end{equation*} 
    We let \( \mathcal{D} \) be the set of diamonds in \( P \), and \( P_{x, y} \) be the set of paths from \( x \) to \( y \).
    The \emph{diamond action} is the function \( - \cdot - \colon \mathcal{D} \times P_{x, y} \to P_{x, y} \) sending a pair \( (D, \gamma) \) to \( D \cdot \gamma \).
\end{dfn}

\begin{dfn} [Diamond transitive oriented graded poset]
    Let \( P \) be a graded poset.
    We say that \( P \) is \emph{diamond transitive} if for all \( x, y \in P \) such that \( x \le y \), the diamond action on the graded poset \( P_{x, y} \) is transitive, that is, for all paths \( \gamma, \gamma' \) from \( x \) to \( y \) in \( P \), there exist \( k \in \mathbb{N} \) and a sequence \( (D_i)_{i = 1}^k \) of diamonds in \( P \) such that \( \gamma' = D_1 \cdot \ldots \cdot D_k \cdot \gamma \).
\end{dfn}

\noindent We learnt the about the following Lemma from Hadzihasanovic.
\begin{lem} \label{lem:diamond_transitive}
    Let \( P \) be a regular directed complex.
    Then the graded poset of \( \augm{P} \) is diamond transitive.
\end{lem}
\begin{proof}
    The underlying graded poset of \( \augm{P} \) is a CW poset by \cite[Corollary 10.3.3]{hadzihasanovic2024combinatorics}.
    We conclude by \cite[Theorem 5.14]{chandler2019thin}.
\end{proof}

\begin{dfn} [Collapsible closed subset] \label{dfn:collapsible}
    Let \( U \) be a molecule, \( K \subseteq U \) be a closed subset, and \( \beta \in \set{-, +} \).
    We say that \( K \) is \emph{\( \beta \)\nbd collapsible} if \( K \) is non-empty and for all \( x \in U \), if \( \bd{0}{-\beta} x \in K \) then \( x \in K \).
    In that case, we let \( \coll K U \) be the oriented graded poset whose underlying set is
    \begin{equation*}
        \set{\zcoll} \coprod \set{\icoll u \mid u \in U \setminus K},
    \end{equation*}
    and oriented graded structure is given by
    \begin{equation*}
        \cofaces{}{\a} x \eqdef
        \begin{cases}
            \set{ \icoll v \mid v \in \cofaces{}{\a} u} & \text{if } x = \icoll u,\\
            \set{ \icoll u \mid \dim u = 1, \faces{}{\a} u \in K} &\text{if } x = \bullet, \a = \beta,\\
            \varnothing &\text{else.}
        \end{cases}
    \end{equation*}
    The underlying poset of \( \coll{K}{U} \) fits into the commutative square
    \begin{equation} \label{tik:square_collapse}
        \begin{tikzcd} 
            K & \pt \\
            U & {\coll K U}
            \arrow[""{name=0, anchor=center, inner sep=0}, two heads, from=1-1, to=1-2]
            \arrow[hook, from=1-1, to=2-1]
            \arrow[hook, from=1-2, to=2-2]
            \arrow[two heads, from=2-1, to=2-2]
        \end{tikzcd}
    \end{equation}
    where \( \pt \to \coll{K}{U} \) picks out the element \( \zcoll \), and \( \mapcoll \colon U \surj \coll{K}{U} \) is the order-preserving surjection defined by
    \begin{equation*}
        x \mapsto
        \begin{cases}
            \icoll x & \text{if } x \in U \setminus K\\
            \zcoll & \text{otherwise.}
        \end{cases}
    \end{equation*}
\end{dfn}

\begin{lem} \label{lem:collapsible_is_puhsout}
    Let \( U \) be a molecule, \( \beta \in \set{-, +} \) and \( K \subseteq U \) be a \( \beta \)\nbd collapsible subset.
    Then the commutative square (\ref{tik:square_collapse}) is a pushout in the category of posets.
\end{lem}
\begin{proof}
    Since the underlying square is a pushout of sets, for the statement to be true, we claim that it is enough that for every element \( u \in U \setminus K \) covering an element \( k \) of \( K \), then either \( \dim u = 1 \), or there exists \( v \in U \setminus K \) such that \( v < u \) and \( v \) covers an element of \( K \).
    Indeed, in that case, the elements covering \( \zcoll \) in \( \coll{K}{U} \) with the universal partial order will be exactly of the form \( \icoll{u} \) for \( u \in U \setminus K \) with \( \dim u = 1 \). 
    Therefore, suppose that \( u \in U \setminus K \) of dimension \( n \geq 2 \) covers an element \( k \) of \( K \).
    We will find \( v < u \) such that \( v \notin K \) but covers an element of \( K \).

    Recall that we can find a path \( \gamma \eqdef u_{-1} \eqdef \bot \to u_0 \to u_1 \to \ldots \to u_n \eqdef u \) in \( \augm{U} \) such that \( u_0 = \bd{0}{-\beta} u \).
    Then, none of the \( u_i \) belong to \( K \), since otherwise, \( u_0 \) would be in \( K \), hence so would be \( u \), since \( K \) is \( \beta \)\nbd collapsible.
    Now pick any path \( \gamma' \eqdef k_{-1} = \bot \to k_1 \to \ldots \to k_{n - 1} \eqdef k \) from \( \bot \) to \( k \) in \( \augm{U} \) which necessarily belong to \( K \), since it is closed.
    By Lemma \ref{lem:diamond_transitive}, there exist \( r \geq 1 \) and a sequence of diamonds 
    \begin{equation*}
        \left(D_i \eqdef \set{z_i < y_i, y'_i < x_i}\right)_{i = 1}^r
    \end{equation*}
    such that \( \gamma = D_r \cdot \ldots \cdot D_1 \cdot \gamma' \).
    Up to swapping \( y_i \) and \( y'_i \), we may assume that \( y'_i = y_{i + 1} \) for all \( i \in \set{1, \ldots, r - 1} \).
    Let \( \ell \eqdef \max \set{i \mid y_i \in K} \), which exists since \( y_1 \in K \).
    If \( x_{\ell} < u \), then we are done since \( x_{\ell} \) covers \( y_{\ell} \in K \).
    Else \( x_{\ell} = u \).
    Then, either \( \ell = r \), in which case \( y'_{\ell} = u_{n - 1} \notin K \), or \( \ell < r \), in which case \( y'_{\ell} = y_{\ell + 1} \notin K \).
    In any case, \( y'_{\ell} \) is not in \( K \).
    Since \( y_{\ell} \in K \) is of dimension \( \geq 1 \) and \( K \) is closed, \( z_{\ell} \in K \).
    Thus we found \( y'_{\ell} < u \) such that \( y'_\ell \) is not in \( K \) and covers \( z_{\ell} \in K \).
    This concludes the proof.
\end{proof}


\begin{lem} \label{lem:path_from_zero_bd_to_all_points}
    Let \( U \) be a molecule, \( \a \in \set{-, +} \) and \( x \in \gr{0}{U} \).
    Then there exists \( k \in \mathbb{N} \) and an inclusion \( \iota \colon k\dglobe{1} \incl U \) such that \( \bd{0}{\a} \iota = \bd{0}{\a} U \) and \( \bd{0}{-\a} \iota = x \).
\end{lem}
\begin{proof}
    We proceed by induction on the submolecules of \( V \) of \( U \).
    The base case where \( \dim V = 0 \) is clear.
    Suppose inductively that the statement is true of all proper submolecules \( V \) of \( U \).
    First suppose that \( U \) is an atom.
    If \( \dim U = 0 \), then the statement is again clear, otherwise \( \dim U > 0 \) and \( x \in \bd{}{\beta} U \) for some \( \beta \in \set{-, +} \).
    We conclude by inductive hypothesis on \( \bd{}{\beta} U \submol U \) and globularity.
    Now suppose \( U \) split into \( V \cp{k} W \), and assume that \( x \in V \), the case \( x \in W \) is symmetrical.
    Then either \( k > 0 \), hence \( \bd{0}{} V = \bd{0}{} U \) and we may conclude by inductive hypothesis on \( V \), or \( k = 0 \).
    If \( \a = - \), then \( \bd{0}{-} V = \bd{0}{-} U \), and we conclude by inductive hypothesis on \( V \) again.
    Else, \( \a = + \) and \( \bd{0}{+} U = \bd{0}{+} W \).
    Consider by inductive hypothesis an inclusion \( \iota \colon k\dglobe{1} \incl V \) from \( x \) to \( \bd{0}{+} V \).
    Then \( \bd{0}{-} W \) is isomorphic to \( k'\dglobe{1} \) for some \( k' > 0 \), hence \( \iota \cp{0} \bd{1}{-} \idd{W} \colon (k + k') \dglobe{1} \incl U \) is the desired inclusion.
\end{proof}

\begin{lem} \label{lem:collapsible_connected_with_all_closure_element}
    Let \( U \) be a molecule, \( \beta \in \set{-, +} \), \( K \subseteq U \) be a \( \beta \)\nbd collapsible subset, and \( V \submol U \).
    Then \( V \cap K \) is either empty or connected.
    In the latter case, \( V \cap K \subseteq V \) is \( \beta \)\nbd collapsible and contains \( \bd{0}{\beta} V \).
\end{lem}
\begin{proof}
    Assume that \( \beta = - \), the case \( \beta = + \) is dual.
    Suppose that \( V \cap K \) is non-empty.
    We show that \( x \eqdef \bd{0}{-} V \) is in \( V \cap K \).
    Let \( z \in V \cap K \), then \( y \eqdef \bd{0}{-} z \in V \cap K \).
    By Lemma \ref{lem:path_from_zero_bd_to_all_points}, there exist \( k \geq 0 \) and \( \iota \colon k\arr \incl V \) such that \( \bd{0}{} \iota = (x, y) \).
    Since \( y = \bd{0}{+} \iota \in K \) and \( K \) is collapsible, \( \cofaces{}{+} y \in K \).
    Since \( K \) is closed, \( \faces{}{-} \cofaces{}{+} y \in K \).
    Iterating this process \( k \) times, we find that \( x \in K \).
    Then, suppose that \( V \cap K = F \cup G \) for two closed subsets \( F, G \) with \( F \cap G = \varnothing \), and suppose without loss of generality that \( x \in F \).
    Let \( y \in \gr{0}{G} \). 
    As previously, we have an inclusion \( \iota \colon k\arr \incl F \cup G \) such that \( \bd{0}{}\iota = (x, y) \).
    Then \( \iota(k\arr) = \invrs{\iota}(F) \cup \invrs{\iota}(G) \) and \( \invrs{\iota}F \cap \invrs{\iota}G = \varnothing \).
    By \cite[Lemma 3.3.13]{hadzihasanovic2024combinatorics}, \( \invrs{\iota}F = \varnothing \) or \( \invrs{\iota}G = \varnothing \), a contradiction.
    This proves that \(  \gr{0}{G} = \varnothing \), thus that \( G = \varnothing \).
    This shows that \( V \cap K \) is connected.
    Finally, let \( x \in V \) such that \( \bd{0}{+} x \in K \).
    Since \( K \) is  \( \beta \)\nbd collapsible, \( x \in V \cap K \).
    Hence \( V \cap K \subseteq V \) is \( \beta \)\nbd collapsible.
    This concludes the proof.
\end{proof}

\begin{lem} \label{lem:collapsible_negbeta_boundary_collapse_all}
    Let \( U \) be a molecule, \( \beta \in \set{-, +} \), and \( K \subseteq U \) be a \( \beta \)\nbd collapsible subset such that \( \bd{0}{-\beta} U \subseteq K \).
    Then \( K = U \).
\end{lem}
\begin{proof}
    We proceed by induction on the layering dimension \( \ell \) of \( U \) (see \cite[Comment 4.2.13]{hadzihasanovic2024combinatorics}).
    If \( \ell = -1 \), then \( U \) is an atom, thus \( U = \clset{\top_U} \subseteq K \) by definition.
    Inductively, let \( \ell \geq 0 \). Then \( U \) admits an \( \ell \)\nbd layering
    \begin{equation*}
        U \eqdef \order{1}{U} \cp{\ell} \ldots \cp{\ell} \order{r}{U}
    \end{equation*}
    with \( r \geq 2 \) such that \( \order{i}{U} \) has layering dimension \( < \ell \) for all \( 1 \le i \le r \).
    Suppose that \( \beta = - \), the case \( \beta = + \) is dual.
    Then \( \bd{0}{+} U = \bd{0}{+} \order{r}{U} \in K \).
    By Lemma \ref{lem:collapsible_connected_with_all_closure_element}, \( \order{r}{U} \cap K \) is \( \beta \)\nbd collapsible, thus by inductive hypothesis, \( \order{r}{U} = \order{r}{U} \cap K \).
    In particular, \( \bd{0}{+} \order{r - 1}{U} \in K \).
    Iterating this process \( r \) times, we find that for all \( i \in \set{0, \ldots, r - 1} \), \( \order{r - i}{U} = \order{r - i}{U} \cap K \).
    Therefore, \( U = U \cap K \).
    This concludes the proof.
\end{proof}

\begin{lem} \label{lem:collapsible_mapcoll_preserve_boundaries}
    Let \( U \) be a molecule, \( \beta \in \set{-, +} \), \( K \subseteq U \) be a \( \beta \)\nbd collapsible subset, \( \a \in \set{-, +} \) and \( k \in \mathbb{N} \).
    Then 
    \begin{equation*}
        \mapcoll (\bd{k}{\a} U) = \bd{k}{\a} (\coll{K}{U}),
    \end{equation*}
    in particular \( \bd{0}{\beta} (\coll{K}{U}) = \set{\zcoll} \).
    Furthermore, \( \coll{K}{U} \) is globular, and if \( U \) is round, so is \( \coll{K}{U} \).
\end{lem}
\begin{proof}
    We assume that \( \beta = - \), the case \( \beta = + \) is dual, and that \( K \) is a proper subset of \( U \), otherwise the statement is trivial.
    Suppose that \( k > 0 \), then
    \begin{equation*}
        \bd{k}{\a} (\coll{K}{U}) = \clos \faces{k}{\a} (\coll{K}{U}) \cup \gr{< k}{\clset{\maxel (\coll{K}{U})}} = \mapcoll(\bd{k}{\a} U) \cup \set{\zcoll}.
    \end{equation*}
    By Lemma \ref{lem:collapsible_connected_with_all_closure_element}, \( \bd{0}{-} U \subseteq K \), and since \( k > 0 \), we have \( \set{\zcoll} = p(\bd{0}{-} U) \subseteq p(\bd{k}{\a} U) \).
    Thus, \(  \mapcoll (\bd{k}{\a} U) = \bd{k}{\a} (\coll{K}{U}) \).

    Next suppose \( k = 0 \) and \( \a = + \).
    Then since \( K \) is a proper subset, \( \set{x} = \bd{0}{+} U \) is not a subset of \( K \) by Lemma \ref{lem:collapsible_negbeta_boundary_collapse_all}. 
    Thus, by construction of \( \coll{K}{U} \), we have \( \mapcoll (\bd{0}{+} U) = \bd{0}{+} (\coll{K}{U}) \).
    The next thing to see is therefore that \( \set{\zcoll} = \bd{0}{-} (\coll{K}{U}) \).
    By construction, \( \cofaces{}{+} \zcoll = \varnothing \), thus we have one inclusion.
    Let \( \icoll{u} \in \gr{0}{(U \setminus K)} \).
    If \( u \in \bd{0}{-} U \) then \( u \in K \) by Lemma \ref{lem:collapsible_connected_with_all_closure_element}, a contradiction.
    Thus, there exists \( v \in \cofaces{}{+} u \), and since \( K \) is closed, \( v \notin K \).
    We find that \( \icoll{v} \in \cofaces{}{+} \icoll{u} \), meaning that \( u \notin \bd{0}{-} (\coll{K}{U}) \).
    This proves that \( \set{\zcoll} = \bd{0}{-} (\coll{K}{U}) \).

    By Lemma \ref{lem:collapsible_is_puhsout}, Lemma \ref{lem:collapsible_connected_with_all_closure_element}, and formal properties, for all closed subsets \( V \subseteq U \) such that \( V \) is a molecule, we have 
    \begin{equation*}
        p(V) \cong
        \begin{cases}
            V & \text{if } V \cap K = \varnothing, \\
            \coll{(V \cap K)}{V} & \text{else}.
        \end{cases}
    \end{equation*}
    Using this and the first part of the proof, one sees that \( \coll{K}{U} \) is globular.

    Last, suppose that \( U \) is round of dimension \( n \geq 0 \).
    Let \( k < n \), and let \( x \in (\bd{k}{-} (\coll{K}{U})) \cap (\bd{k}{+} (\coll{K}{U})) \).
    We must show that \( x \in \bd{k - 1}{}  (\coll{K}{U}) \).
    Suppose first that \( x = \zcoll \), then \( \set{x} = \bd{0}{-} (\coll{K}{U}) \).
    If \( k > 0 \) we are done by globularity.
    Else \( k = 0 \).
    In that case, \( \zcoll \in \bd{0}{+} (\coll{K}{U}) \), so \( \bd{0}{+} U \subseteq K \), hence \( \coll{K}{U} = \pt \) by Lemma \ref{lem:collapsible_negbeta_boundary_collapse_all}.
    Thus, \( n = 0 = k \), contradiction.
    Suppose now that \( x = \icoll{u} \) for some \( u \in U \setminus K \).
    By the first part of the proof, \( u \in \bd{k}{-} U \cap \bd{k}{+} U \), and since \( U \) is round, \( u \in \bd{k - 1}{} U \), so that by the first part of the proof again, \( \icoll{u} \in \bd{k - 1}{} (\coll{K}{U}) \).
    This concludes the proof.
\end{proof}

\begin{prop} \label{prop:collapsible_collapse_to_molecules}
    Let \( U \) be a molecule, \( \beta \in \set{-, +} \) and \( K \subseteq U \) be a \( \beta \)\nbd collapsible subset.
    Then \( \coll{K}{U} \) is a molecule and the canonical map \( \mapcoll \colon U \surj \coll{K}{U} \) is a map of molecules.
\end{prop}
\begin{proof}
    Recall that a map of poset \( L \to \pt \) is final when seen as a functor just when \( L \) is connected. 
    Let \( \mapcoll \colon U \surj \coll{K}{U} \) be the canonical map.
    Let \( V \submol U \) be a submolecule of \( U \). 
    If \( V \cap K = \varnothing \), then \( \restr{\mapcoll}{V} \colon V \surj \mapcoll(V) \) is the identity.
    Otherwise, by Lemma \ref{lem:collapsible_is_puhsout}, the diagram
    \begin{center}
        \begin{tikzcd}
            {V \cap K} & \pt \\
            V & {p(V)}
            \arrow[""{name=0, anchor=center, inner sep=0}, two heads, from=1-1, to=1-2]
            \arrow[from=1-1, to=2-1]
            \arrow[from=1-2, to=2-2]
            \arrow[two heads, from=2-1, to=2-2]
            \arrow["\lrcorner"{anchor=center, pos=0.125, rotate=180}, draw=none, from=2-2, to=0]
        \end{tikzcd}
    \end{center}
    is a pushout.
    By Lemma \ref{lem:collapsible_connected_with_all_closure_element}, \( V \cap K \) is connected, thus \( V \cap K \surj \pt \) is final.
    Since final functors are stable under pushouts, we obtain that \( \restr{\mapcoll}{V} \colon V \surj \mapcoll(V) \) is final.
    This proves that for all submolecules \( V \submol U \), \( \restr{\mapcoll}{V} \colon V \surj \mapcoll(V) \) is final.
    Now let \( x \in U \), \( k \geq 0 \) and \( \a \in \set{-, +} \).
    Using either the fact that \( \restr{p}{\bd{k}{\a} x} \) is the identity if \( \clset{x} \cap K = \varnothing \) and Lemma \ref{lem:collapsible_mapcoll_preserve_boundaries} otherwise, we find that \( \mapcoll(\bd{k}{\a} x) = \bd{k}{\a} \mapcoll(x) \).
    This proves that, in case \( \coll{K}{U} \) is a regular directed complex, \( \mapcoll \) is a map of regular directed complexes.

    We prove by induction on the submolecules \( V \) of \( U \) that \( \mapcoll(V) \) is a molecule.
    The base case where \( V \) is a point is clear.
    Suppose inductively that \( \mapcoll(V) \) is a molecule for all proper submolecules \( V \) of \( U \).
    Suppose first that \( U \) is an atom.
    By inductive hypothesis and Lemma \ref{lem:collapsible_mapcoll_preserve_boundaries}, for all \( \a \in \set{-, +} \), \( p(\bd{}{\a} U) \) is a round molecule.
    Thus, \( p(\bd{}{-} U) \celto p(\bd{}{+} U) \) is a well-defined atom, and one sees that, unless \( K = U \), it is by construction isomorphic to \( \coll{K}{U} \).
    If \( K = U \), then \( U = \pt \) is also an atom. 
    This shows that \( \coll{K}{U} \) is an atom.
    Now suppose that \( U \) is a molecule.
    Then by inductive hypothesis, \( \coll{K}{U} \) is a regular directed complex.
    We conclude by \cite[Proposition 6.2.33]{hadzihasanovic2024combinatorics} and the first part of the proof that it is in fact a molecule.
\end{proof}

\begin{lem} \label{lem:has_two_point_is_susp}
    Let \( U \) be a molecule such that \( \gr{0}{U} = \bd{0}{-} U \coprod \bd{0}{+} U \).
    Then \( U = \sus{U'} \) for some molecule \( U' \).
\end{lem}
\begin{proof}
    We proceed by induction on the submolecules \( V \) of \( U \).
    The base case where \( V \) is a point is vacuously true, since \( \gr{0}{V} \) has exactly one element.
    Suppose inductively that the statement is true of all proper submolecules of \( U \).
    Consider first the case where \( U \) is an atom.
    We distinguish two cases.
    Either \( U \) is \( \dglobe{1} \), in which case it is \( \sus{\pt} \) and we are done, or \( U \) is of the form \( V \celto W \) with \( \dim V = \dim W \geq 1 \).
    In the latter case,
    \begin{align} 
         \bd{0}{} V \subseteq \gr{0}{V} \subseteq \gr{0}{U} &= \bd{0}{} U = \bd{0}{} V, \text{ and} \nonumber\\
         \bd{0}{-} V \cap \bd{0}{+} V &= \varnothing \label{aln:grade_boundary_zero}.
    \end{align}
    Thus, \( \gr{0}{V} = \bd{0}{-} V \coprod \bd{0}{+} V\).
    Similarly, \( \gr{0}{W} = \bd{0}{-} W \coprod \bd{0}{+} W \).
    By inductive hypothesis on the submolecules, \( V = \sus{V'} \) and \( W = \sus{W'} \) for some molecules \( V' \) and \( W' \).
    By \cite[Proposition 7.3.16]{hadzihasanovic2024combinatorics}, \( U \) is of the form \( \sus{(V' \celto W')} \).
    Suppose next that \( U \) splits into \( V \cp{k} W \) with \( \dim V, \dim W > k \).
    If \( k = 0 \), then \( \bd{0}{+} V \subseteq \gr{0}{U} \), but \( \bd{0}{+} V \cap (\bd{0}{-} U \coprod \bd{0}{+} U) \) is empty, contradicting the assumption.
    Thus, \( k > 0 \) and (\ref{aln:grade_boundary_zero}) also holds of \( V \) and \( W \).
    We deduce by inductive hypothesis that \( V = \sus{V'} \) and \( W = \sus{W'} \).
    By \cite[Proposition 7.3.16]{hadzihasanovic2024combinatorics} again, \( U \) is of the form \( \sus{(V' \cp{k - 1} W')} \).
    This concludes the proof.
\end{proof}

\begin{prop} \label{prop:desuspension}
    Let \( U \) be a molecule, and \( K^-, K^+ \subseteq U \) be disjoint closed subsets of \( U \) such that \( \gr{0}{U} \subseteq K^- \cup K^+ \), \( K^- \cup K^+ \) is a proper subset of \( U \), and for all \( \a \in \set{-, +} \), \( K^\beta \subseteq U \) is \( \beta \)\nbd collapsible.
    Then there exists a molecule \( V \), together with a commutative diagram
    \begin{center}
        \begin{tikzcd}
            {K^- \coprod K^+} & {\pt \coprod \pt} \\
            U & {\sus{V}}
            \arrow[two heads, from=1-1, to=1-2]
            \arrow[hook', from=1-1, to=2-1]
            \arrow["{{(\bot^-, \bot^+)}}", hook', from=1-2, to=2-2]
            \arrow["q"', two heads, from=2-1, to=2-2]
        \end{tikzcd}
    \end{center}
    whose underlying diagram in \( \Pos \) is a pushout, and such that \( q \) is a map of molecules.
\end{prop}
\begin{proof}
    By Proposition \ref{prop:collapsible_collapse_to_molecules}, we have a map of molecules \( p \colon U \surj \coll{K^-}{U} \), and since \( K^+ \subseteq U \) is \( + \)\nbd collapsible, so is \( p(K^+) \subseteq \coll{K^-}{U} \).
    Applying Proposition \ref{prop:collapsible_collapse_to_molecules} again, we have a map of molecules \( q \colon U \surj W \), which is the pushout of the map \( K^- \coprod K^- \surj \pt \coprod \pt \) of regular directed complexes along the inclusion \( K^+ \coprod K^- \incl U \).
    By Lemma \ref{lem:collapsible_mapcoll_preserve_boundaries}, the inclusion \( \pt \coprod \pt \incl W \) has image \( \bd{0}{} W \).
    To conclude, we need to show that \( W = \sus{V} \) for some molecule \( V \).
    Since \( q \) is a surjective map of molecules, 
    \begin{equation*}
        \gr{0}{W} = q(\gr{0}{U}) \subseteq q(K^-) \cup q(K^+) = \set{\bot^-, \bot^+}
    \end{equation*}
    We conclude by Lemma \ref{lem:has_two_point_is_susp}.
\end{proof}

\begin{thm} \label{thm:suspension_of_stricter}
    Let \( C \) be a stricter \( \omega \)\nbd category.
    Then \( \sus{C} \) is a stricter \( \omega \)\nbd category.
\end{thm}
\begin{proof}
    We use the second characterisation in Lemma \ref{lem:stricter_iff_local_wrt_pasting}.
    Let \( U \) be a molecule and \( \set{\F_x \colon \molecin{\imel{U}{x}} \to \sus{C}}_{x \in U} \) be a \( U \)\nbd matching family in \( \sus{C} \).
    For \( \beta \in \set{-, +} \), let \( K^\beta \eqdef \set{x \in U \mid \pcell{\F_x} = \bot^\beta} \).
    Suppose that there exists \( \beta \in \set{-, +} \) such that \( K^\beta \) is empty and let \( x \in U \).
    If \( \pcell{\F_x} \in C \), we would have \( x \in K^\beta \).
    Thus, \( \pcell{\F_x} = \bot^{-\beta} \), and \( K^{-\beta} = U \).
    Therefore, the candidate amalgamation \( \F \colon \molecin{U} \to \sus{C} \) is well-defined since it factors as
    \begin{equation*}
        \molecin{U} \to \molecin{\pt} \to \sus{C},
    \end{equation*}
    where \( \molecin{\pt} \to \sus{C} \) classifies \( \bot^{-\beta} \).

    Now suppose that \( K^- \) and \( K^+ \) are non-empty.
    Let \( \beta \in \set{-, +} \), then we claim that \( K^\beta \subseteq U \) is \( \beta \)\nbd collapsible.
    Let \( x \in U \), and suppose that \( \bd{0}{-\beta} x \in K^\beta \).
    Then \( \bd{0}{-\beta} \pcell{F_x} = \bot^{\beta} \).
    If \( \pcell{\F_x} \neq \bot^\beta \), then by construction of \( \sus{C} \), \( \bd{0}{-\beta} \pcell{\F_x} = \bot^{-\beta} \), a contradiction.
    Thus, \( \pcell{\F_x} = \bot^\beta \), hence \( x \in K^\beta \).
    Since \( K^\beta \) is non-empty, it is \( \beta \)\nbd collapsible.
    Then  \( \gr{0}{U} \subseteq K^- \cup K^+ \), and \( K^- \cap K^+ = \varnothing \).
    By \cite[Lemma 3.3.13]{hadzihasanovic2024combinatorics}, \( U \) is connected, thus the inclusion \( K^- \cup K^+ \subseteq U \) is proper.
    Now Proposition \ref{prop:desuspension} applies, and we have in particular a molecule \( V \) and a final map of molecules \( q \colon U \surj \sus{V} \). 
    Then, one checks that the family of globular cells of \( C \)
    \begin{equation*}
        \set{\pcell{\F_x} \mid q(x) = \sus{y}}_{y \in V}
    \end{equation*} 
    defines, as per Remark \ref{rmk:data_matching family}, a \( V \)\nbd matching family \( \set{\G_y \colon \molecin{\imel{V}{y}} \to C}_{y \in V} \) in \( C \).
    Since \( C \) is stricter, it admits a well-defined amalgamation \( \G \colon \molecin{V} \to C \).
    Finally, the candidate amalgamation \( \F \colon \molecin{U} \to \sus{C} \) is well-defined, since it factors as \( \F = \sus{\G} \after \molecin{q} \).
    Thus, \( \sus{C} \) is local with respect to \( s_U \).
    This concludes the proof.
\end{proof}

\begin{dfn} [Bipointed stricter \( \omega \)\nbd category]
    A \emph{bipointed stricter \( \omega \)\nbd category} is given by a stricter \( \omega \)\nbd category \( C \) together with a pair of objects \( (a, b) \).
    We let \( \bpt\somegaCat \) be the category of bipointed stricter \( \omega \)\nbd categories and strict functors that respect the bipointing.
\end{dfn}

\begin{cor} \label{cor:adjunction_hom_suspension}
    There is an adjunction
    \begin{equation*}
        \sus{} \colon \somegaCat \leftrightarrows \bpt\somegaCat \cocolon \hom,
    \end{equation*}
    where \( \sus{C} \) is the suspension of \( C \) bipointed by \( (\bot^-, \bot^+) \), and \( \hom(C, a, b) \) is given by \( C(a, b) \).
    Furthermore, the functor
    \begin{equation*}
        \sus{} \colon \somegaCat \to \somegaCat
    \end{equation*}
    preserves connected colimits.
\end{cor}
\begin{proof}
    That the pair of functors is well-defined follows from Lemma \ref{lem:hom_of_stricter_is_stricter} and Theorem \ref{thm:suspension_of_stricter}.
    That this form an adjunction follows from standard arguments.
    Last, since \( \bpt\somegaCat \) is a coslice construction, \( \sus{} \colon \somegaCat \to \somegaCat \) preserves connected colimits by \cite[Proposition 3.3.8]{riehl2019context}.
\end{proof}

